### 2023-02-15 outputs/paper/paper.qmd
Adding inputs and other edits

---
title: "paper"
format: html
editor: visual
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#install.packages('haven')
library(haven)
raw_data <- read_dta("inputs/data/survey.dta")
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

### 2023-02-15 00-simulation.R
Initial commit of script files

@@ -3,6 +3,8 @@ set.seed(3)
 #participant values used in analysis in relation to survey scores
 wave = sample(x = 1:4, size = 5, replace = TRUE)
 age = sample(x = 1:90, size = 5, replace = TRUE)
+male = sample(x = 0:1, size = 5, replace = TRUE)
+
 
 #important survey scores
 only_means = sample(x = 1:5, size = 5, replace = TRUE)

### 2023-02-16 scripts/00-simulation.R
Work on scripts, creating output folder for raw csv and clean csv files

@@ -1,19 +1,18 @@
 set.seed(3)
 
 #participant values used in analysis in relation to survey scores
-wave = sample(x = 1:4, size = 5, replace = TRUE)
-age = sample(x = 1:90, size = 5, replace = TRUE)
-male = sample(x = 0:1, size = 5, replace = TRUE)
+age <- sample(x = 1:90, size = 100, replace = TRUE)
+male <- sample(x = 0:1, size = 100, replace = TRUE)
 
 
 #important survey scores
-only_means = sample(x = 1:5, size = 5, replace = TRUE)
-condemn = sample(x = 1:5, size = 5, replace = TRUE)
-justified = sample(x = 1:5, size = 5, replace = TRUE)
-message = sample(x = 1:5, size = 5, replace = TRUE)
-prevent = sample(x = 1:5, size = 5, replace = TRUE)
+only_means <- sample(x = 1:5, size = 100, replace = TRUE)
+condemn <- sample(x = 1:5, size = 100, replace = TRUE)
+justified <- sample(x = 1:5, size = 100, replace = TRUE)
+message <- sample(x = 1:5, size = 100, replace = TRUE)
+prevent <- sample(x = 1:5, size = 100, replace = TRUE)
 
-df_s = data.frame(
+df_s <- data.frame(
   wave = wave,
   age = age,
   only_means = only_means,

### 2023-02-16 scripts/01-test.R

@@ -1,0 +1,10 @@
+#checking bounds
+min(df_s$age) < 0
+max(df_s$age) > 110
+
+#checking that number of unique row values is appropriate
+length(unique(df_s$wave)) > 4
+
+#checking for allowed col types
+!is.numeric(df_s$only_means)
+any((df_s$only_means | df_s$condemn | df_s$justified | df_s$message | df_s$prevent)%%1!=0)

### 2023-02-16 scripts/02-download.R

@@ -1,0 +1,12 @@
+#loading packages
+library(readstata13)
+library(readr)
+
+#reading in the stata file
+dat <- read.dta13(here::here("inputs/data/survey.dta"))
+
+#limiting the data to just 4th wave surveys
+dat_use <- dat[dat$wave == 4, ]
+
+#writing to csv
+write_csv(dat_use, here::here("outputs/data/survey_W4.csv"))

### 2023-02-16 scripts/02-download.R
changed acquire to clean in script to satisfy co-author

@@ -1,3 +1,12 @@
+#### Preamble ####
+# Purpose: Downloads and saves the data from spotify
+# Author: Finn Korol, Jayden Jung, Sofia Sellitto [...UPDATE THIS...]
+# Data: [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
 #loading packages
 library(readstata13)
 library(readr)
@@ -5,8 +14,5 @@ library(readr)
 #reading in the stata file
 dat <- read.dta13(here::here("inputs/data/survey.dta"))
 
-#limiting the data to just 4th wave surveys
-dat_use <- dat[dat$wave == 4, ]
-
 #writing to csv
-write_csv(dat_use, here::here("outputs/data/survey_W4.csv"))
+write_csv(dat, here::here("outputs/data/survey.csv"))

### 2023-02-16 scripts/03-clean.R

@@ -1,0 +1,21 @@
+#### Preamble ####
+# Purpose: cleaning and preparing data for use
+# Author: Finn Korol, Jayden Jung, Sofia Sellitto 
+# Data: [...UPDATE THIS...]
+# Contact: [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+library(readr)
+library(dplyr)
+library(janitor)
+datc <- read_csv(here::here("outputs/data/survey.csv"), show_col_types = FALSE)
+
+#limiting the data to just 4th wave surveys
+
+dat_use <- datc[datc$wave == 4, ] |> 
+  select(res_id,gender, age, MateComp.cont, pop_15_44_muni_gendergap_2015, jobComp.cont, LifeSatis.cont, hate_violence_means, hate_pol_message, hate_prevent_settlement, hate_polcondemn)
+
+#writing to csv
+write_csv(dat_use, here::here("outputs/data/survey_W4.csv"))

### 2023-02-16 outputs/paper/paper.qmd
Testing reading in data

@@
 #install.packages('haven')
+#install.packages('here')
+
+library(here)
 library(haven)
-raw_data <- read_dta("inputs/data/survey.dta")
+
+raw_data <- read_dta(here::here("inputs/data/survey.dta"))
+
+dat_male <- dat_use[dat_use$gender == "Male"
+
+raw_data$gender
+
+raw_data <- raw_data[raw_data$gender == "Male"]
 ```

### 2023-02-16 scripts/02-download.R
cleaning unused variables from set

@@ -15,4 +15,4 @@ library(readr)
 dat <- read.dta13(here::here("inputs/data/survey.dta"))
 
 #writing to csv
-write_csv(dat, here::here("outputs/data/survey.csv"))
+write_csv(dat, here::here("inputs/data/survey.csv"))

### 2023-02-16 scripts/03-clean.R

@@ -10,12 +10,12 @@
 library(readr)
 library(dplyr)
 library(janitor)
-datc <- read_csv(here::here("outputs/data/survey.csv"), show_col_types = FALSE)
+datc <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
 #limiting the data to just 4th wave surveys
-
-dat_use <- datc[datc$wave == 4, ] |> 
-  select(res_id,gender, age, MateComp.cont, pop_15_44_muni_gendergap_2015, jobComp.cont, LifeSatis.cont, hate_violence_means, hate_pol_message, hate_prevent_settlement, hate_polcondemn)
+#14,44, east, res_id, 
+dat_use <- datc[datc$wave == 4, ] |>
+  subset(select = -c(res_id, east, singdivsep, refugee_ind))
 
 #writing to csv
-write_csv(dat_use, here::here("outputs/data/survey_W4.csv"))
+write_csv(dat_use, here::here("inputs/data/survey_W4.csv"))

### 2023-02-16 scripts/03-clean.R
removing more variables

@@ -15,7 +15,7 @@ datc <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 #limiting the data to just 4th wave surveys
 #14,44, east, res_id, 
 dat_use <- datc[datc$wave == 4, ] |>
-  subset(select = -c(res_id, east, singdivsep, refugee_ind))
+  subset(select = -c(res_id, east, singdivsep, refugee_ind, list))
 
 #writing to csv
 write_csv(dat_use, here::here("inputs/data/survey_W4.csv"))

### 2023-02-17 outputs/paper/paper.qmd
Add signature for test
YAML updates

@@
 ---
-title: "paper"
-format: html
-editor: visual
+title: "Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed"
+author: "Jayden Jung, Finn Korol, Sofia Sellitto"
+thanks: "Code and data are available at: https://github.com/jj-andj/mate-comp-hate ; Replication on Social Science Reproduction platform available at: "
+date: "February 17, 2023"
+date-format: long
+format: 
+  pdf: 
+    documentclass: article
+    geometry: margin = 1in
+    abstract: "Globalization, immigration, and asylum seeking is a common topic of discussion, one which most people hold some personal opinion on accompanied by certain justifications.
+This paper analyzes data on what proportion of non-immigrant German men are likely to perceive refugees as threats to finding a romantic partner relative to the male-to-female ratio within their municipality and which of them support sentiments of anti-refugee violence.
+Results show that there can be argued an effect of these sentiments on actual rates of hate crime.
+We apply secondary research regarding Canadian rates of immigration and gender imbalances and raise concerns regarding the possibly generalizable nature of the findings in Germany.
+As this issue specifically affects minority groups experiencing prejudice and even furthers their marginalization, we place great emphasis on the weight of this discussion and propose that it should be considered to inform policies or initiatives intending to address racism and hate crimes, especially in breaking down the framing of refugees as a threat to non-immigrants, whether that's through education, public messaging, or other implementations."
+
+output: 
+  bookdown::pdf_document2
+toc: false
+fig_caption: yes
+nocite: '@*'
+bibliography: references.bib
+header-includes: \definecolor{ltgray}{HTML}{EFEFEF}
 ---
@@
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.
+Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>. Sofia was here! ahdkjwandlkwn
 
@@
 
-raw_data <- read_dta(here::here("inputs/data/survey.dta"))
+#raw_data <- read_dta(here::here("inputs/data/survey.dta"))
 
-dat_male <- dat_use[dat_use$gender == "Male"
+#dat_male <- dat_use[dat_use$gender == "Male"
 
-raw_data$gender
+#raw_data$gender
 
-raw_data <- raw_data[raw_data$gender == "Male"]
+#raw_data <- raw_data[raw_data$gender == "Male"]
 ```

### 2023-02-17 outputs/paper/paper.qmd
Paper edits

@@
 As this issue specifically affects minority groups experiencing prejudice and even furthers their marginalization, we place great emphasis on the weight of this discussion and propose that it should be considered to inform policies or initiatives intending to address racism and hate crimes, especially in breaking down the framing of refugees as a threat to non-immigrants, whether that's through education, public messaging, or other implementations."
+    number-sections: true
 
@@
 
-## Quarto
+# Introduction
 
@@
 
-## Running Code
+# Running Code
 
@@
 The `echo: false` option disables the printing of code (only output is displayed).
+
+\clearpage
+
+# References

### 2023-02-17 outputs/paper/paper.qmd
Paper Edits

@@
 ```{r}
+#| echo: false
 #install.packages('haven')
@@
 
-#raw_data <- read_dta(here::here("inputs/data/survey.dta"))
-
-#dat_male <- dat_use[dat_use$gender == "Male"
-
-#raw_data$gender
-
-#raw_data <- raw_data[raw_data$gender == "Male"]
+#survey_data <- read_dta(here::here("inputs/data/survey_cleaned.csv"))
 ```
-
-You can add options to executable code like this
-
-```{r}
-#| echo: false
-2 * 2
-```
-
-The `echo: false` option disables the printing of code (only output is displayed).
 
@@
 
-# References
+# References {.unnumbered}

### 2023-02-17 outputs/paper/paper.qmd
Add Introduction

@@
 
+In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals (cite stat gen Canada).
+Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,1250 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents (cite immigration-refugees-citizenship & macrotrends.net).
+
+There are many factors that contribute to the increase in hate crimes in Canada.
+However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada.
+These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
+Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets.
+A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research (cite research paper).
+
+In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women (cite research paper).
+Their finding suggest that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets (cite research paper).
+By using ecological evidence and originally cucrrated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increase anti-refugee sentiments and violence (cite research paper).
+
+Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
+In addressing the following two research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of german politicians, we conclude that \_\_\_\_\_\_\_\_INSERT CONCLUSION HERE\_\_\_\_\_.
+
+We will first discuss \_\_\_\_\_\_\_\_INSERT FORMT HERE\_\_\_\_\_\_\_\_\_\_
+
 # Running Code

### 2023-02-17 outputs/paper/paper.qmd
Edited intro and updated references

--- 2023-02-17 outputs/paper/paper.qmd
@@
 author: "Jayden Jung, Finn Korol, Sofia Sellitto"
-thanks: "Code and data are available at: https://github.com/jj-andj/mate-comp-hate ; Replication on Social Science Reproduction platform available at: "
+thanks: "Code and data are available at: https://github.com/jj-andj/mate-comp-hate ; Replication on Social Science Reproduction platform available at: https://doi.org/10.48152/ssrp-qg85-cb34"
 date: "February 17, 2023"
@@
 
-Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>. Sofia was here! ahdkjwandlkwn
+In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
+Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,1250 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022].
+
+There are many factors that contribute to the increase in hate crimes in Canada.
+However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada.
+These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
+Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets.
+A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research [@main_paper].
+
+In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
+Their finding suggest that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
+By using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increase anti-refugee sentiments and violence [@main_paper].
+
+Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
+In addressing the following two research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians, we conclude that \_\_\_\_\_\_\_\_INSERT CONCLUSION HERE\_\_\_\_\_.
+
+We will first discuss \_\_\_\_\_\_\_\_INSERT FORMT HERE\_\_\_\_\_\_\_\_\_\_
 

### 2023-02-17 outputs/paper/paper.qmd
Add estimand

@@
 In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
-Their finding suggest that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
+Their findings for the estimand of non-immigrant German men suggest that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
 By using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increase anti-refugee sentiments and violence [@main_paper].

### 2023-02-17 outputs/paper/paper.qmd
Add setup

@@
 #| echo: false
-#install.packages('haven')
+#install.packages('readr')
 #install.packages('here')
+# install.packages("readstata13")  #  readstata13_0.9.2
+# install.packages("MASS") # MASS_7.3-51.6  
+# install.packages("sandwich")  # sandwich_2.5-1 
+# install.packages("lmtest") # lmtest_0.9-37 
+# install.packages("pBrackets") # pBrackets_1.0
 
-library(here)
-library(haven)
+library(readr) # read_csv
+library(here) # here
+library(readstata13) #  readstata13_0.9.2
+library(MASS) # MASS_7.3-51.6  
+library(sandwich)  # sandwich_2.5-1 
+library(lmtest) # lmtest_0.9-37  
+library(pBrackets) # pBrackets_1.0
 

### 2023-02-17 outputs/paper/paper.qmd
Edit paper

@@
 
-```{r}
+```{r setup}
 #| echo: false
-#install.packages('readr')
-#install.packages('here')
+#| message: false
+#| warning: false
+# install.packages('readr')
+# install.packages('here')
 # install.packages("readstata13")  #  readstata13_0.9.2

### 2023-02-17 scripts/00-simulation.R
updates to simulation script

@@ -1,23 +1,120 @@
+#### Preamble ####
+# Purpose: Simulation of our prepared dataframe
+# Author: Finn Korol, Jayden Jung, Sofia Sellitto
+# Data: [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
 set.seed(3)
 
 #participant values used in analysis in relation to survey scores
 age <- sample(x = 1:90, size = 100, replace = TRUE)
-male <- sample(x = 0:1, size = 100, replace = TRUE)
-
+# data used for our figures will only be from waves 2 and 4 of surveying
+wave <- sample(c(2,4), size = 100, replace = TRUE)
+age_group <- sample(c('18-29','30-39','40-49','50-59','60 and older'), size = 100, replace = TRUE)
+gender <- sample(c('Male','Female'), size = 100, replace = TRUE)
+state <- sample(c('State A','State B', 'State C', 'State D'), size = 100, replace = TRUE)
+citizenship <- sample(x = 0:1, size = 100, replace = TRUE)
+marital <- sample(c('widowed', 'married', 'commonlaw', 'single', 'divorced/separated'), size = 100, replace = TRUE)
+religion <- sample(c('catholic christian', 'protestant christian', 'jewish', 'muslim', 'nondenominational', 'atheist', 'agnostic', 'Eastern Religion'), size = 100, replace = TRUE)
+occupation <- sample(c('student', 'unemployed', 'retired', 'civil servant', 'self-employed', 'sick/on leave', 'employee'), size = 100, replace = TRUE)
+income <- sample(c('under 500', '500-1500', '1500-2500', '2500-3500', '3500-4500', '4500-5500', 'over 5500'), size = 100, replace = TRUE)
+household_size <- sample(x = 0:10, size = 100, replace = TRUE)
 
 #important survey scores
-only_means <- sample(x = 1:5, size = 100, replace = TRUE)
-condemn <- sample(x = 1:5, size = 100, replace = TRUE)
-justified <- sample(x = 1:5, size = 100, replace = TRUE)
[…]

### 2023-02-17 scripts/01-test.R

@@ -1,10 +1,19 @@
+#### Preamble ####
+# Purpose: Example unit tests run on simulated data
+# Author: Finn Korol, Jayden Jung, Sofia Sellitto
+# Data: [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
 #checking bounds
-min(df_s$age) < 0
-max(df_s$age) > 110
+min(df_s$age, na.rm=TRUE) < 0
+max(df_s$age, na.rm=TRUE) > 110
 
 #checking that number of unique row values is appropriate
 length(unique(df_s$wave)) > 4
 
 #checking for allowed col types
-!is.numeric(df_s$only_means)
+!is.numeric(df_s$only_means, na.rm=TRUE)
 any((df_s$only_means | df_s$condemn | df_s$justified | df_s$message | df_s$prevent)%%1!=0)

### 2023-02-17 scripts/02-download.R

@@ -1,6 +1,6 @@
 #### Preamble ####
 # Purpose: Downloads and saves the data from spotify
-# Author: Finn Korol, Jayden Jung, Sofia Sellitto [...UPDATE THIS...]
+# Author: Finn Korol, Jayden Jung, Sofia Sellitto 
 # Data: [...UPDATE THIS...]
 # Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
 # License: MIT

### 2023-02-17 scripts/03-clean.R

@@ -13,9 +13,9 @@ library(janitor)
 datc <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
 #limiting the data to just 4th wave surveys
-#14,44, east, res_id, 
-dat_use <- datc[datc$wave == 4, ] |>
-  subset(select = -c(res_id, east, singdivsep, refugee_ind, list))
+dat_use <- datc[(datc$wave == 4 | datc$wave == 2), ] |>
+  subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role))
+  rename(only_means = )
 
 #writing to csv
-write_csv(dat_use, here::here("inputs/data/survey_W4.csv"))
+write_csv(dat_use, here::here("inputs/data/survey_clean.csv"))

### 2023-02-17 scripts/01-test.R
Correcting tests to return true when pass

@@ -7,13 +7,14 @@
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
 
-#checking bounds
-min(df_s$age, na.rm=TRUE) < 0
-max(df_s$age, na.rm=TRUE) > 110
+#checking bound minimum
+min(df_s$age, na.rm=TRUE) > 0
+
+#checking bound maximum
+max(df_s$age, na.rm=TRUE) < 110
 
 #checking that number of unique row values is appropriate
-length(unique(df_s$wave)) > 4
+length(unique(df_s$wave)) < 4
 
 #checking for allowed col types
-!is.numeric(df_s$only_means, na.rm=TRUE)
-any((df_s$only_means | df_s$condemn | df_s$justified | df_s$message | df_s$prevent)%%1!=0)
+any((df_s$only_means | df_s$condemn | df_s$justified | df_s$message | df_s$prevent)%%1==0)

### 2023-02-17 scripts/00-simulation.R
Create simulation csv for test

@@ -7,6 +7,8 @@
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
 
+library(here)
+library(readr)
 
 set.seed(3)
 
@@ -69,7 +71,7 @@ excess_males <- runif(100, 0.5, 2)
 treatment_list <- sample(c('scenario 1', 'scenario 2'), size = 100, replace = TRUE)
 outcome_list <- sample(x = 0:4, size = 100, replace = TRUE)
 
-df_s <- data.frame(
+survey_sim <- data.frame(
   age,
   wave,
   age_group,
@@ -118,3 +120,5 @@ df_s <- data.frame(
   treatment_list,
   outcome_list
   )
+
+write_csv(survey_sim, here::here("inputs/data/survey_sim.csv"))

### 2023-02-17 scripts/01-test.R

@@ -7,14 +7,17 @@
 # Pre-requisites: [...UPDATE THIS...]
 # Any other information needed? [...UPDATE THIS...]
 
+survey_sim <- read_csv(here::here("inputs/data/survey_sim.csv"), 
+                       show_col_types = FALSE)
+
 #checking bound minimum
-min(df_s$age, na.rm=TRUE) > 0
+min(survey_sim$age, na.rm=TRUE) > 0
 
 #checking bound maximum
-max(df_s$age, na.rm=TRUE) < 110
+max(survey_sim$age, na.rm=TRUE) < 110
 
 #checking that number of unique row values is appropriate
-length(unique(df_s$wave)) < 4
+length(unique(survey_sim$wave)) < 4
 
 #checking for allowed col types
-any((df_s$only_means | df_s$condemn | df_s$justified | df_s$message | df_s$prevent)%%1==0)
+any((survey_sim$only_means | survey_sim$condemn | survey_sim$justified | survey_sim$message | survey_sim$prevent)%%1==0)

### 2023-02-17 scripts/03-clean.R
renaming cols

@@ -10,12 +10,24 @@
 library(readr)
 library(dplyr)
 library(janitor)
-datc <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
+survey <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
 #limiting the data to just 4th wave surveys
-dat_use <- datc[(datc$wave == 4 | datc$wave == 2), ] |>
-  subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role))
-  rename(only_means = )
-
+survey_reduced_renamed <- datc[(datc$wave == 4 | datc$wave == 2), ] |>
+  subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role)) |>
+  rename(only_means = hate_violence_means,
+         message = hate_pol_message,
+         prevent = hate_prevent_settlement,
+         condemn = hate_polcondemn,
+         justified = hate_justified,
+         mate_compete = MateComp.cont,
+         job_compete = JobComp.cont,
+         life_satisfaction = LifeSatis.cont,
+         excess_males = pop_15_44_muni_gendergap_2015,
+         muslim_aff = muslim_ind,
+         afd_aff = afd_ind,
+         contact_aff = contact_ind
+         )
+  
 #writing to csv
-write_csv(dat_use, here::here("inputs/data/survey_clean.csv"))
+write_csv(survey_reduced_renamed, here::here("inputs/data/survey_clean.csv"))

### 2023-02-17 scripts/03-clean.R
preamble writing

@@ -1,11 +1,10 @@
 #### Preamble ####
-# Purpose: cleaning and preparing data for use
+# Purpose: Cleaning data on survey results prior to analysis. Data frame is reduced (unneeded columns, waves), columns are renamed for clarity and consistency.
 # Author: Finn Korol, Jayden Jung, Sofia Sellitto 
-# Data: [...UPDATE THIS...]
-# Contact: [...UPDATE THIS...]
+# Data: survey.csv
+# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: run 02-download.R
 
 library(readr)
 library(dplyr)

### 2023-02-17 scripts/00-simulation.R
Updating preambles and comments

@@ -1,11 +1,9 @@
 #### Preamble ####
-# Purpose: Simulation of our prepared dataframe
-# Author: Finn Korol, Jayden Jung, Sofia Sellitto
-# Data: [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulating data on survery results 
+# Authors: Finn Korol, Jayden Jung, Sofia Sellitto
+# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: none
 
 library(here)
 library(readr)
@@ -121,4 +119,5 @@ survey_sim <- data.frame(
   outcome_list
   )
 
+# write simulation onto csv for testing
 write_csv(survey_sim, here::here("inputs/data/survey_sim.csv"))

### 2023-02-17 scripts/01-test.R

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: Example unit tests run on simulated data
+# Purpose: Testing simulated survey data
 # Author: Finn Korol, Jayden Jung, Sofia Sellitto
-# Data: [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Data: survey_sim.csv
+# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Have run 00-simulation.R and have survey_sim.csv saved
 
+# read in simulation file
 survey_sim <- read_csv(here::here("inputs/data/survey_sim.csv"), 
                        show_col_types = FALSE)
 

### 2023-02-17 scripts/03-clean.R
notes

@@ -11,7 +11,7 @@ library(dplyr)
 library(janitor)
 survey <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
-#limiting the data to just 4th wave surveys
+#limiting the data to just 4th wave surveys, subsetting to only columns used in analysis and renaming columns 
 survey_reduced_renamed <- datc[(datc$wave == 4 | datc$wave == 2), ] |>
   subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role)) |>
   rename(only_means = hate_violence_means,

### 2023-02-17 scripts/03-clean.R
bug fix

@@ -12,7 +12,7 @@ library(janitor)
 survey <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
 #limiting the data to just 4th wave surveys, subsetting to only columns used in analysis and renaming columns 
-survey_reduced_renamed <- datc[(datc$wave == 4 | datc$wave == 2), ] |>
+survey_reduced_renamed <- survey[(survey$wave == 4 | survey$wave == 2), ] |>
   subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role)) |>
   rename(only_means = hate_violence_means,
          message = hate_pol_message,

### 2023-02-17 outputs/paper/paper.qmd
Read in data
planning of document figures

@@
 
-#survey_data <- read_dta(here::here("inputs/data/survey_cleaned.csv"))
+survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
 ```
 
+##Figure 1
+not including p value, percentage bar graph, detailed explanation of tercile meanings 
+```{r}
+
+```
+
+##Figure 2
+add prevent bar
+```{r}
+
+```
+
+##Table 1
+have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)
+```{r}
+
+```
 \clearpage

### 2023-02-17 outputs/paper/paper.qmd
edits

--- 2023-02-17 outputs/paper/paper.qmd
@@
 In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
-Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,1250 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022].
+Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022].
 
@@
 
+# Data
+
+# Results
+
+# Discussion 
+## Findings 
+## Implications 
+## Ethical Implications 
+## Limitations 
+## Future Research
+
 \clearpage

### 2023-02-17 outputs/paper/paper.qmd
Paper edits

--- 2023-02-17 outputs/paper/paper.qmd
@@
 
-#survey_data <- read_dta(here::here("inputs/data/survey_cleaned.csv"))
+survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
+```
+
+##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings
+
+```{r}
+
+```
+
+##Figure 2 add prevent bar
+
+```{r}
+
+```
+
+##Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)
+
+```{r}
+
 ```

### 2023-02-17 outputs/paper/paper.qmd
Paper edits

@@
 ```{r}
+#| label: fig-excess
+#| fig-cap: "look at deez"
+#| echo: false
+#| message: false
+#| warning: false
 
@@
 ```{r}
+#| label: fig-statements
+#| fig-cap: "look at dat"
+#| echo: false
+#| message: false
+#| warning: false
+
+survey_2 <- survey_data[survey_data$wave == 2,]
 
@@
 
-##Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)
+\## Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)
 
 ```{r}
+#| label: tbl-mate
+#| fig-cap: "look at dat"
+#| echo: false
+#| message: false
+#| warning: false
 

### 2023-02-17 scripts/00-simulation.R
Updating preamble

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: Simulation of our prepared dataframe
-# Author: Finn Korol, Jayden Jung, Sofia Sellitto
-# Data: [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Simulating data on survery results 
+# Authors: Finn Korol, Jayden Jung, Sofia Sellitto
+# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: none
 
+library(here)
+library(readr)
 
 set.seed(3)
 
@@ -69,7 +69,7 @@ excess_males <- runif(100, 0.5, 2)
 treatment_list <- sample(c('scenario 1', 'scenario 2'), size = 100, replace = TRUE)
 outcome_list <- sample(x = 0:4, size = 100, replace = TRUE)
 
-df_s <- data.frame(
+survey_sim <- data.frame(
   age,
   wave,
   age_group,
@@ -118,3 +118,6 @@ df_s <- data.frame(
   treatment_list,
   outcome_list
   )
+
+# write simulation onto csv for testing
+write_csv(survey_sim, here::here("inputs/data/survey_sim.csv"))

### 2023-02-17 scripts/01-test.R

@@ -1,20 +1,23 @@
 #### Preamble ####
-# Purpose: Example unit tests run on simulated data
+# Purpose: Testing simulated survey data
 # Author: Finn Korol, Jayden Jung, Sofia Sellitto
-# Data: [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Data: survey_sim.csv
+# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Have run 00-simulation.R and have survey_sim.csv saved
+
+# read in simulation file
+survey_sim <- read_csv(here::here("inputs/data/survey_sim.csv"), 
+                       show_col_types = FALSE)
 
 #checking bound minimum
-min(df_s$age, na.rm=TRUE) > 0
+min(survey_sim$age, na.rm=TRUE) > 0
 
 #checking bound maximum
-max(df_s$age, na.rm=TRUE) < 110
+max(survey_sim$age, na.rm=TRUE) < 110
 
 #checking that number of unique row values is appropriate
-length(unique(df_s$wave)) < 4
+length(unique(survey_sim$wave)) < 4
 
 #checking for allowed col types
-any((df_s$only_means | df_s$condemn | df_s$justified | df_s$message | df_s$prevent)%%1==0)
+any((survey_sim$only_means | survey_sim$condemn | survey_sim$justified | survey_sim$message | survey_sim$prevent)%%1==0)

### 2023-02-17 scripts/02-download.R

@@ -1,18 +1,17 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from spotify
+# Purpose: Downloads and saves survey data to new file
 # Author: Finn Korol, Jayden Jung, Sofia Sellitto 
-# Data: [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Data: survey.dta
+# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Have downloaded survey.dta from https://doi.org/10.7910/DVN/QXJDJ5
 
 #loading packages
 library(readstata13)
 library(readr)
 
 #reading in the stata file
-dat <- read.dta13(here::here("inputs/data/survey.dta"))
+survey <- read.dta13(here::here("inputs/data/survey.dta"))
 
 #writing to csv
-write_csv(dat, here::here("inputs/data/survey.csv"))
+write_csv(survey, here::here("inputs/data/survey.csv"))

### 2023-02-17 scripts/03-clean.R

@@ -1,21 +1,32 @@
 #### Preamble ####
-# Purpose: cleaning and preparing data for use
+# Purpose: Cleaning data on survey results prior to analysis. Data frame is reduced (unneeded columns, waves), columns are renamed for clarity and consistency.
 # Author: Finn Korol, Jayden Jung, Sofia Sellitto 
-# Data: [...UPDATE THIS...]
-# Contact: [...UPDATE THIS...]
+# Data: survey.csv
+# Contact: finn.korol@mail.utoronto.ca, jayden.jung@mail.utoronto.ca, sofia.sellitto@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: run 02-download.R
 
 library(readr)
 library(dplyr)
 library(janitor)
-datc <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
+survey <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
-#limiting the data to just 4th wave surveys
-dat_use <- datc[(datc$wave == 4 | datc$wave == 2), ] |>
-  subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role))
-  rename(only_means = )
-
+#limiting the data to just 4th wave surveys, subsetting to only columns used in analysis and renaming columns 
+survey_reduced_renamed <- survey[(survey$wave == 4 | survey$wave == 2), ] |>
+  subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role)) |>
+  rename(only_means = hate_violence_means,
+         message = hate_pol_message,
+         prevent = hate_prevent_settlement,
+         condemn = hate_polcondemn,
+         justified = hate_justified,
+         mate_compete = MateComp.cont,
+         job_compete = JobComp.cont,
+         life_satisfaction = LifeSatis.cont,
+         excess_males = pop_15_44_muni_gendergap_2015,
+         muslim_aff = muslim_ind,
+         afd_aff = afd_ind,
+         contact_aff = contact_ind
+         )
+  
 #writing to csv
-write_csv(dat_use, here::here("inputs/data/survey_clean.csv"))
+write_csv(survey_reduced_renamed, here::here("inputs/data/survey_clean.csv"))

### 2023-02-17 scripts/03-clean.R
adjusting variable names

@@ -23,9 +23,9 @@ survey_reduced_renamed <- survey[(survey$wave == 4 | survey$wave == 2), ] |>
          job_compete = JobComp.cont,
          life_satisfaction = LifeSatis.cont,
          excess_males = pop_15_44_muni_gendergap_2015,
-         muslim_aff = muslim_ind,
-         afd_aff = afd_ind,
-         contact_aff = contact_ind
+         muslim_att = muslim_ind,
+         afd_att = afd_ind,
+         contact_att = contact_ind
          )
   
 #writing to csv

### 2023-02-17 scripts/03-clean.R
renaming variables

@@ -25,7 +25,8 @@ survey_reduced_renamed <- survey[(survey$wave == 4 | survey$wave == 2), ] |>
          excess_males = pop_15_44_muni_gendergap_2015,
          muslim_att = muslim_ind,
          afd_att = afd_ind,
-         contact_att = contact_ind
+         contact_att = contact_ind,
+         left_right = lrscale
          )
   
 #writing to csv

### 2023-02-17 outputs/paper/paper.qmd
Edits

--- 2023-02-17 outputs/paper/paper.qmd
@@
 # install.packages("pBrackets") # pBrackets_1.0  
+# install.packages("dplyr") 
+# install.packages("tidyverse")
 
@@
 library(lmtest) # lmtest_0.9-37  
-library(pBrackets) # pBrackets_1.0
+library(dplyr)
+library(tidyverse)
+library(jtools)
+library(huxtable)
 
-#survey_data <- read_dta(here::here("inputs/data/survey_cleaned.csv"))
+survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
 ```
@@
 # Data 
+## Source
+The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany (cite paper).
+Our reproduction seeks to address two claims made from the original paper and apply a Canadian facing lens.
+The two claims are as follows:
+(1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
+(2) Are non-immigrant German men who perceive mate competition more likely to support violence as the only means to gain the attention of German politicians?
+To collect this data, the original paper uses four waves of online survey data collected in Germany that are representative of gender, age and state (geographic location) [@main_paper].
 
-# Results
+## Methodology 
+This paper will replicate the survey data that was originally collected for the 2021 paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned.
+Using the online survey platform “Respondi”, they conduct four waves of surveys which spanned from September 2016 to December 2017 [@main_paper].
+The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully.
+[@main_paper].
+To mitigate potential biases, the researchers employed list experiments in Waves 1 and 2, and in Wave 2, they randomly assigned 50% of the sample to either a control or treatment group.
+The treatment group was exposed to statements concerning their agreement with using violence against refugees as a means to get the attention of German politicians.
+However, no evidence was found to suggest that respondents were concealing their support for hate crimes when comparing the means of the control and treatment groups [@main_paper].
+
+## Features
+
+The original survey data assessed participants on 53 variables, being representative of gender, age and state.
+The range of recorded age data from the survey occurs from 19-89 years old.
+Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older.
+Both male and female participants took part in the survey, but females were only involved in the second and fourth waves of surveys.
+The survey was distributed across 16 German states.
+Our reproduction, however, included removing variables that were not utilized in our final reproduction analysis and included only the necessary Waves 2 and 4.
+As a part of our reproduction, we also simplified the names of variables to make them easier to work with.
+From the original data, each variable correlates with a survey question asked to participants.
+To discuss the variables used in our reproduction I have grouped them in the following way and have listed each variable below.
+
+Sociodemographics:
+* Age Group
+* Gender
+* State
+* German Citizen 
+* Marital Status 
+* Relationship status, single
+* Religious Affiliation 
+* Education
+* Occupation
+* Income 
+* Household Size 
+* Subjective Social Status 
+* Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
+* Politics: left and right-leaning 
+* Politics: affiliated parties
+
+Mate Competition: using a scale of agree or disagree
+* Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
+
+Job Competition: using a scale of agree or disagree  
+* The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
+
+Life Satisfaction: scale of 0-10 
+* Satisfaction with life
+
+Encountering Refugees
+* How many KM is the closest refugee reception center from your home 
+* How many refugees do you believe have settled in your municipality in the last year 
+* In the last month, how many refugees have you encountered in the following locations
+
+Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree 
+* Violence is sometimes the only means that citizens have to get the attention of German politicians 
+* Attitudes towards Muslims
+* Hostility against refugees justified
+* Politicians should condemn attacks against refugees
+* Racist violence is defensible if it leads to fewer refugees settling in a town 
+* Attacks against refugee homes are sometimes necessary to make garner the attention of politicians 
+* Refugee integration in Germany 
+* German refugees should be entitled to German citizenship 
+* The number of refugees should be reduced 
+* Refugees are receiving more than non-immigrant Germans 
+* Refugees should give up their culture to adopt that of Germany 
+* Refugees are good for the economy 
+* Refugees increase crime 
+* Increased refugees increase the risk of terrorism 
+* Will additional refugees in your town increase the influence of Islam (local)
+* Will additional refugees in your town be a challenge for local schools (local)
+* Will additional refugees in your town increase competition for housing (local) 
+* Will additional refugees in your town change the way of life in your town (local)
+
+Operational category 
+* Experiement lists
+* Treatement lists
+* Outcome lists 
+* Waves: out of 4
+
+>>>>>>> b03039f (Create figure 1)
 
@@
 ## Ethical Implications 
+=======
+## Methodology
+>>>>>>> b03039f (Create figure 1)
+
+# Results
+
+# Discussion
+
+## Findings
+
+## Implications
+
+## Ethical Implications
+
+In their paper, Dancygier, Egami, Jamal, and Rischke examine the ethical implication of using experimental methodologies to investigate their research topic.
+By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence.
+By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment, which might have been a possible outcome had trials been conducted [@main_paper].
+While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate.
+By being presented with a platform to express their perception of mate competition and if they agree that violence towards refugees is the only way to garner the attention of German politicians, respondents may feel that their opinions are incorrectly justified.
+This then has the potential to translate to violence towards German refugees.
+
+## Accounting for Bias
+
+Ethical implications and biases arise naturally when collecting quantitative and qualitative data.
+In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper].
+The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms.
+However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper].
+Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest.
+One method to control for this bias is simple random sampling, where participants are chosen by chance.
+Meaning that every individual in the population/ estimand has an equal chance of being selected.
+However, in their study, they were unable to utilize simple random sampling.
+Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and state/ geographical region [@main_paper}.
+Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].
+
 ## Limitations
+
 ## Future Research
+
+======= ##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings ======= ##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings
+
+```{r}
+
+```
+
+```{r}
+#| label: fig-excess
+#| fig-cap: "look at deez"
+#| echo: false
+#| message: false
+#| warning: false
+
+survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
+
+# Subset of people from wave 4 and select needed columns
+s_exc <- survey_data[survey_data$wave == 4 ,]
+s_exc <- select(s_exc, c(gender, age, mate_compete, excess_males))
+s_exc <- na.omit(s_exc)
+
+# Add value for mate competition tercile
+s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)
+s_exc$terc <- ifelse(s_exc$excess_males < 1.04, "1st Tercile", ifelse(s_exc$excess_males < 1.12, "2nd Tercile", "3rd Tercile"))
+
+# Create age groups for all people, men bw 18-44, and men bw 30-40
+s_exc$agroup <- "All, Men & Women"
+
+s_exc2 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 44 & s_exc$age >= 18,]
+s_exc2$agroup <- "Male 18-44"
+
+s_exc3 <- s_exc[s_exc$gender == "Male" & s_exc$age <= 40 & s_exc$age >= 30,]
+s_exc3$agroup <- "Male 30-40"
+
+# Combining data frame back together
+s_excm <- rbind(s_exc, s_exc2)
+s_exct <- rbind(s_excm, s_exc3)
+
+# Calculating proportion 
+mean_all <- tapply(s_exc$matecomp, s_exc$terc, mean)
+mean_2 <- tapply(s_exc2$matecomp, s_exc2$terc, mean)
+mean_3 <- tapply(s_exc3$matecomp, s_exc3$terc, mean)
+
+# Setting up data frame for plotting
+s1 <- data.frame(c(mean_all))
+colnames(s1) <- c("mean")
+s2 <- data.frame(c(mean_2))
+colnames(s2) <- c("mean")
+s3 <- data.frame(c(mean_3))
+colnames(s3) <- c("mean")
+
+s_m <- rbind(s1, s2)
+s_tot <- rbind(s_m, s3)
+
+rownames(s_tot) <- NULL
+
+s_tot$grp <- rep(c("All, Men & Women","Men 18-44","Men 30-40"),each=3)
+s_tot$terc <- rep(c("1st Tercile","2nd Tercile","3rd Tercile"),times=3)
+
+# Plotting
+wrapper <- function(x, ...) 
+{paste(strwrap(x, ...), collapse = "\n")}
+
+s_tot %>% 
+  ggplot(aes(x=terc, y=mean, group=grp, fill=grp)) +
+  geom_col(position = "dodge")+
+  labs(x="Terciles of Excess Male Rate", fill = "Group") +
+  labs(y = wrapper("Proportion perceiving refugees as mate competition", width = 30)) +
+  theme_minimal() +
+  theme(legend.position="bottom") +
+  theme(text=element_text(size=11, family="serif")) +
+  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =70)) +
+  theme(plot.title = element_text(face = "bold"))
+```
+
+##Figure 2 add prevent bar
+
+```{r}
+#| label: fig-statements
+#| fig-cap: "look at dat"
+#| echo: false
+#| message: false
+#| warning: false
+
+survey_w2 <- survey_data[survey_data$wave == 2,]
+
+```
+
+##Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)
+
+```{r}
+#| label: tbl-mate
+#| fig-cap: "look at dat"
+#| echo: false
+#| message: false
+#| warning: false
+
+survey_w4 <- survey_data[survey_data$wave == 4,]
+
+lm1 <- lm(only_means ~ mate_compete, data=survey_w4)
+summary(lm1)
+
+lm2 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction, data=survey_w4)
+summary(lm2)
+
+lm3 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
+            factor(age_group) +     # age group
+            factor(gender) +     # gender 
+            factor(state) +     # state  
+            factor(citizenship) +    # german citizen
+            factor(marital) +    # marital status
+            factor(religion) +    # religious affiliation
+            eduyrs +    # education
+            factor(occupation) +    # main activity
+            factor(income) +   # income
+            factor(household_size) +   # household size
+            factor(self_econ),    # subjective social status
+          data=survey_w4)
+summary(lm3)
+
+lm4 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
+            factor(age_group) +   # age group
+            factor(gender) +   # gender 
+            factor(state) +   # state  
+            factor(citizenship) +  # german citizen
+            factor(marital) +  # marital status
+            factor(religion) +  # religious affiliation
+            eduyrs +  # education
+            factor(occupation) +  # main activity
+            factor(income) + # income
+            factor(household_size) + # household size
+            factor(self_econ) + # subjective social status
+            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
+            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
+            factor(ref_economy) + factor(ref_crime) + factor(ref_terror),
+          data=survey_w4)
+summary(lm4)
+
+lm5 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction + 
+            factor(age_group) +      # age group
+            factor(gender) +      # gender 
+            factor(state) +      # state  
+            factor(citizenship) +     # german citizen
+            factor(marital) +     # marital status
+            factor(religion) +     # religious affiliation
+            eduyrs + # education
+            factor(occupation) +     # main activity
+            factor(income) +    # income
+            factor(household_size) +    # household size
+            factor(self_econ) +    # subjective social status
+            factor(ref_integrating) + # Refugee Index (National-level; Q73) 8 in total
+            factor(ref_citizenship) + factor(ref_reduce) + factor(ref_moredone) + factor(ref_cultgiveup) + 
+            factor(ref_economy) + factor(ref_crime) + factor(ref_terror) + 
+            factor(ref_loc_services) +    # Refugee Index (Local, Q75)
+            factor(ref_loc_economy) + factor(ref_loc_crime) + factor(ref_loc_culture) + factor(ref_loc_islam) + 
+            factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife), ## end
+          data=survey_w4)
+summary(lm5)
+
+# Add More Variables 
+# lrscale  Q21  Left-Right Scale
+# afd, Q23  Closeness to AfD
+# muslim_ind, afd_ind, contact_ind
+# distance_ref Q71. Distance to refugee reception centers
+# settle_ref Q72. Settlement of refugees living in area
+
+formula.5 <- 
+  as.character("only_means ~ mate_compete + job_compete + 
+               life_satisfaction +  factor(age_group) + factor(gender) + 
+               factor(state) + factor(citizenship) + factor(marital) + 
+               factor(religion) + eduyrs + factor(occupation) + 
+               factor(income) + factor(household_size) + factor(self_econ) + 
+               factor(ref_integrating) + factor(ref_citizenship) + factor(ref_reduce) + 
+               factor(ref_moredone) + factor(ref_cultgiveup) + 
+               factor(ref_economy) + factor(ref_crime) + factor(ref_terror)  + 
+               factor(ref_loc_services) +  factor(ref_loc_economy) + factor(ref_loc_crime) + 
+               factor(ref_loc_culture) + factor(ref_loc_islam) + 
+               factor(ref_loc_schools) + factor(ref_loc_housing) + factor(ref_loc_wayoflife)")
+
+formula.6 <- paste(formula.5, "factor(distance_ref) + factor(settle_ref)", 
+                   "left_right + afd + muslim_att + afd_att + contact_att", 
+                   sep="+", collapse="+")
+
+lm6 <- lm(as.formula(formula.6), data=survey_w4)
+summary(lm6)
+
+table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
+  set_escape_contents(FALSE) |>
+  insert_row(c("sociodemographics \n", " ", " ", "X", "X", "X", "X"), after = 7) |>
+  insert_row(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
+  insert_row(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
+  insert_row(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)
+
+table1
+
+```
 

### 2023-02-18 outputs/paper/paper.qmd
Paper edits

@@
 # Data
+
 ## Source
+
 The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany (cite paper).
 Our reproduction seeks to address two claims made from the original paper and apply a Canadian facing lens.
-The two claims are as follows:
-(1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
+The two claims are as follows: (1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
 (2) Are non-immigrant German men who perceive mate competition more likely to support violence as the only means to gain the attention of German politicians?
@@
 ## Methodology
+
 This paper will replicate the survey data that was originally collected for the 2021 paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned.
-Using the online survey platform “Respondi”, they conduct four waves of surveys which spanned from September 2016 to December 2017 [@main_paper].
+Using the online survey platform "Respondi", they conduct four waves of surveys which spanned from September 2016 to December 2017 [@main_paper].
 The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully.
@@
 Sociodemographics:
-* Age Group
-* Gender
-* State
-* German Citizen 
-* Marital Status 
-* Relationship status, single
-* Religious Affiliation 
-* Education
-* Occupation
-* Income 
-* Household Size 
-* Subjective Social Status 
-* Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
-* Politics: left and right-leaning 
-* Politics: affiliated parties
+
+-   Age Group
+
+-   Gender
+
+-   State
+
+-   German Citizen
+
+-   Marital Status
+
+-   Relationship status, single
+
+-   Religious Affiliation
+
+-   Education
+
+-   Occupation
+
+-   Income
+
+-   Household Size
+
+-   Subjective Social Status
+
+-   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
+
+-   Politics: left and right-leaning
+
+-   Politics: affiliated parties
 
 Mate Competition: using a scale of agree or disagree
-* Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
+
+-   Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
 
 Job Competition: using a scale of agree or disagree
-* The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
+
+-   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
 
 Life Satisfaction: scale of 0-10
-* Satisfaction with life
+
+-   Satisfaction with life
 
 Encountering Refugees
-* How many KM is the closest refugee reception center from your home 
-* How many refugees do you believe have settled in your municipality in the last year 
-* In the last month, how many refugees have you encountered in the following locations
+
+-   How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations
 
 Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree
-* Violence is sometimes the only means that citizens have to get the attention of German politicians 
-* Attitudes towards Muslims
-* Hostility against refugees justified
-* Politicians should condemn attacks against refugees
-* Racist violence is defensible if it leads to fewer refugees settling in a town 
-* Attacks against refugee homes are sometimes necessary to make garner the attention of politicians 
-* Refugee integration in Germany 
-* German refugees should be entitled to German citizenship 
-* The number of refugees should be reduced 
-* Refugees are receiving more than non-immigrant Germans 
-* Refugees should give up their culture to adopt that of Germany 
-* Refugees are good for the economy 
-* Refugees increase crime 
-* Increased refugees increase the risk of terrorism 
-* Will additional refugees in your town increase the influence of Islam (local)
-* Will additional refugees in your town be a challenge for local schools (local)
-* Will additional refugees in your town increase competition for housing (local) 
-* Will additional refugees in your town change the way of life in your town (local)
+
+-   Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims
+
+-   Hostility against refugees justified
+
+-   Politicians should condemn attacks against refugees
+
+-   Racist violence is defensible if it leads to fewer refugees settling in a town
+
+-   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians
+
+-   Refugee integration in Germany
+
+-   German refugees should be entitled to German citizenship
+
+-   The number of refugees should be reduced
+
+-   Refugees are receiving more than non-immigrant Germans
+
+-   Refugees should give up their culture to adopt that of Germany
+
+-   Refugees are good for the economy
+
+-   Refugees increase crime
+
+-   Increased refugees increase the risk of terrorism
+
+-   Will additional refugees in your town increase the influence of Islam (local)
+
+-   Will additional refugees in your town be a challenge for local schools (local)
+
+-   Will additional refugees in your town increase competition for housing (local)
+
+-   Will additional refugees in your town change the way of life in your town (local)
 
 Operational category
-* Experiement lists
-* Treatement lists
-* Outcome lists 
-* Waves: out of 4
 
->>>>>>> b03039f (Create figure 1)
+-   Experiment lists
+
+-   Treatment lists
+
+-   Outcome lists
+
+-   Waves: out of 4
 
 # Discussion
+
 ## Findings
+
 ## Implications
-## Ethical Implications 
-=======
+
+# Ethical Implications
+
 ## Methodology
->>>>>>> b03039f (Create figure 1)
 
@@
   theme(text=element_text(size=11, family="serif")) +
-  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =70)) +
+  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =60)) +
   theme(plot.title = element_text(face = "bold"))
@@
 
-survey_w2 <- survey_data[survey_data$wave == 2,]
+survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
+
+s_stmt <- survey_data[survey_data$wave == 2,]
+s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified, list, treatment_list))
+
+s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
+s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
+s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
+s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)
+
+s_stmtmeans <- s_stmt %>% 
+  na.omit(meansp)
+meansp <- mean(s_stmt$meansp)
+msgp <- mean(s_stmt$msgp)
+prevp <- mean(s_stmt$prevp)
+justp <- mean(s_stmt$justp)
 
@@
 #| warning: false
+#| include: false
 

### 2023-02-18 scripts/03-clean.R
Fixing clean data

@@ -13,8 +13,8 @@ survey <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
 #limiting the data to just 4th wave surveys, subsetting to only columns used in analysis and renaming columns 
 survey_reduced_renamed <- survey[(survey$wave == 4 | survey$wave == 2), ] |>
-  subset(select = -c(res_id, east, singdivsep, refugee_ind, list, women_role)) |>
-  rename(only_means = hate_violence_means,
+  subset(select = -c(res_id, east, singdivsep, refugee_ind, women_role)) |>
+  dplyr::rename(only_means = hate_violence_means,
          message = hate_pol_message,
          prevent = hate_prevent_settlement,
          condemn = hate_polcondemn,

### 2023-02-18 scripts/03-clean.R
Fix cleaning

@@ -13,7 +13,7 @@ survey <- read_csv(here::here("inputs/data/survey.csv"), show_col_types = FALSE)
 
 #limiting the data to just 4th wave surveys, subsetting to only columns used in analysis and renaming columns 
 survey_reduced_renamed <- survey[(survey$wave == 4 | survey$wave == 2), ] |>
-  subset(select = -c(res_id, east, singdivsep, refugee_ind, women_role)) |>
+  subset(select = -c(res_id, east, singdivsep, refugee_ind, women_role, list, treatment_list)) |>
   dplyr::rename(only_means = hate_violence_means,
          message = hate_pol_message,
          prevent = hate_prevent_settlement,

### 2023-02-18 outputs/paper/paper.qmd
New figure added

@@
 # install.packages("tidyverse")
+# install.packages("list)
 
@@
 library(huxtable)
+library(list)
 
@@
 
+# Add indicator if respondent agrees/strongly agrees that refugees are mate threats
+s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)
+
 # Add value for mate competition tercile
-s_exc$matecomp <- ifelse(s_exc$mate_compete >= 3, 1, 0)
 s_exc$terc <- ifelse(s_exc$excess_males < 1.04, "1st Tercile", ifelse(s_exc$excess_males < 1.12, "2nd Tercile", "3rd Tercile"))
@@
 
-# Calculating proportion 
+# Calculating proportion of respondents who agree or strongly agree by tercile
 mean_all <- tapply(s_exc$matecomp, s_exc$terc, mean)
@@
 
+# Set up, filter for wave 2 and select needed columns
 survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
@@
 s_stmt <- survey_data[survey_data$wave == 2,]
-s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified, list, treatment_list))
+s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified))
 
+# Add column with value for people agreeing or strongly agreeing
 s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
 s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
+s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)
 s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
-s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)
+s_stmt$conp <- ifelse(s_stmt$condemn >= 3, 1, 0)
 
-s_stmtmeans <- s_stmt %>% 
-  na.omit(meansp)
-meansp <- mean(s_stmt$meansp)
+# Calculate proportion of respondents to agree/strongly agree with given statement
+s_stmtmeans <- na.omit(s_stmt$meansp)
+meansp <- mean(s_stmtmeans)
+
 msgp <- mean(s_stmt$msgp)
+justp <- mean(s_stmt$justp)
 prevp <- mean(s_stmt$prevp)
-justp <- mean(s_stmt$justp)
+conp <- mean(s_stmt$conp)
 
+# Data frame prepped for plotting
+s_stmt_p <- data.frame(c(meansp, msgp, justp, prevp, conp))
+s_stmt_p$stmt <- c("Only means", "Message", "Justified", "Prevent", "Condemn")
+
+colnames(s_stmt_p) <- c("pptn", "stmt")
+
+# Plotting
+wrapper <- function(x, ...) 
+{paste(strwrap(x, ...), collapse = "\n")}
+
+s_stmt_p %>% 
+  ggplot(aes(x=stmt, y=pptn)) +
+  geom_col(fill="gray", colour="black") +
+  scale_x_discrete(limits = c("Only means", "Message", "Justified", "Prevent", "Condemn")) +
+  labs(x="Statement") +
+  labs(y = wrapper("Proportion of respondents", width = 40)) +
+  theme_minimal() +
+  theme(text=element_text(size=11, family="serif")) +
+  ggtitle(wrapper("13% to 25% of respondents agree with statements supporting or not condemning violence against refugees", width =60)) +
+  theme(plot.title = element_text(face = "bold"))
+
+# add note for condemn
 ```

### 2023-02-19 outputs/paper/paper.qmd
New figures and tables

@@
 
+```{r setup}
+#| echo: false
+#| message: false
+#| warning: false
+# install.packages('readr')
+# install.packages('here')
+# install.packages("readstata13")  #  readstata13_0.9.2
+# install.packages("MASS") # MASS_7.3-51.6  
+# install.packages("sandwich")  # sandwich_2.5-1 
+# install.packages("lmtest") # lmtest_0.9-37 
+# install.packages("pBrackets") # pBrackets_1.0  
+# install.packages("dplyr") 
+# install.packages("tidyverse")
+# install.packages("list)
+# install.packages("knitr")
+# install.packages("kableExtra")
+
+library(readr) # read_csv
+library(here) # here
+library(readstata13) #  readstata13_0.9.2
+library(MASS) # MASS_7.3-51.6  
+library(sandwich)  # sandwich_2.5-1 
+library(lmtest) # lmtest_0.9-37  
+library(dplyr)
+library(tidyverse)
+library(jtools)
+library(huxtable)
+library(list)
+library(knitr)
+library(kableExtra)
+```
+
 # Introduction
@@
 We will first discuss \_\_\_\_\_\_\_\_INSERT FORMT HERE\_\_\_\_\_\_\_\_\_\_
-
-# Running Code
-
-When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:
-
-```{r setup}
-#| echo: false
-#| message: false
-#| warning: false
-# install.packages('readr')
-# install.packages('here')
-# install.packages("readstata13")  #  readstata13_0.9.2
-# install.packages("MASS") # MASS_7.3-51.6  
-# install.packages("sandwich")  # sandwich_2.5-1 
-# install.packages("lmtest") # lmtest_0.9-37 
-# install.packages("pBrackets") # pBrackets_1.0  
-# install.packages("dplyr") 
-# install.packages("tidyverse")
-# install.packages("list)
-
-library(readr) # read_csv
-library(here) # here
-library(readstata13) #  readstata13_0.9.2
-library(MASS) # MASS_7.3-51.6  
-library(sandwich)  # sandwich_2.5-1 
-library(lmtest) # lmtest_0.9-37  
-library(dplyr)
-library(tidyverse)
-library(jtools)
-library(huxtable)
-library(list)
-
-survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
-```
 
@@
 
+\clearpage
+
+\renewcommand{\arraystretch}{2}
+
 ```{r}
+#| label: tbl-terc
+#| tbl-cap: "Dividing respondents into three terciles by their municipality's gender ratio"
+#| echo: false
+#| message: false
+#| warning: false
 
+terc_table <- data.frame(
+  tercile = c("1st Tercile", "2nd Tercile", "3rd Tercile"),
+  ratio = c("Less than 1.04", 
+               "More than 1.04, Less than 1.12",
+               "More than 1.12")
+)
+
+terc_table %>% 
+  knitr::kable(booktabs = T, col.names = c("Tercile", "Municipality's Male to Female Ratio")) %>% 
+  column_spec(1, bold = T, width = "10em") %>%
+  column_spec(2, width = "20em")
 ```
@@
 #| label: fig-excess
-#| fig-cap: "look at deez"
+#| fig-cap: "Proportion of respondents who see refugees as a mating threat by age group and tercile"
 #| echo: false
@@
   ggplot(aes(x=terc, y=mean, group=grp, fill=grp)) +
-  geom_col(position = "dodge")+
+  geom_col(position = "dodge", colour = "black")+
   labs(x="Terciles of Excess Male Rate", fill = "Group") +
@@
 
-##Figure 2 add prevent bar
+\clearpage
+
+```{r}
+#| label: tbl-stmt
+#| tbl-cap: "Statements used for surveying respondents"
+#| echo: false
+#| message: false
+#| warning: false
+
+stmt_table <- data.frame(
+  type = c("Only means", "Message", "Justified", "Prevent", "Condemn"),
+  question = c("When it comes to the refugee problem, violence is sometimes the only means that citizens have to get the attention of German politicians.", 
+               "Attacks against refugee homes are sometimes necessary to make it clear to politicians that we have a refugee problem.",
+               "Hostility against refugees is sometimes justified, even when it ends up in violence.",
+               "Xenophobic acts of violence are defensible if they result in fewer refugees settling in town.", 
+               "Politicians should condemn attacks against refugees more forcefully.
+(For this statement, the results were reversed such that we are looking at respondents who Disagreed or Strongly Disagreed)")
+)
+
+stmt_table %>% 
+  knitr::kable(booktabs = T, col.names = c("Type", "Statement")) %>% 
+  column_spec(1, bold = T, width = "7em") %>%
+  column_spec(2, width = "35em")
+```
 
@@
 #| label: fig-statements
-#| fig-cap: "look at dat"
+#| fig-cap: "Proportion of respondents who agree with varying hate crime support statements"
 #| echo: false
@@
   scale_x_discrete(limits = c("Only means", "Message", "Justified", "Prevent", "Condemn")) +
-  labs(x="Statement") +
+  labs(x="Statement Type") +
   labs(y = wrapper("Proportion of respondents", width = 40)) +
@@
 
-##Table 1 have it coded in completely (check marks), better description of meanings, labels of models (model1, model2,...)
+\renewcommand{\arraystretch}{1.5}
 
@@
 #| label: tbl-mate
-#| fig-cap: "look at dat"
+#| tbl-cap: "Perceiving refugees as mate competition predicts support for hate crime"
 #| echo: false
@@
 #| warning: false
-#| include: false
+
+survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
 
@@
 lm1 <- lm(only_means ~ mate_compete, data=survey_w4)
-summary(lm1)
 
 lm2 <- lm(only_means ~ mate_compete + job_compete + life_satisfaction, data=survey_w4)
-summary(lm2)
 
@@
           data=survey_w4)
-summary(lm3)
 
@@
           data=survey_w4)
-summary(lm4)
 
@@
           data=survey_w4)
-summary(lm5)
 
@@
 lm6 <- lm(as.formula(formula.6), data=survey_w4)
-summary(lm6)
 
-table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
-  set_escape_contents(FALSE) |>
-  insert_row(c("sociodemographics \n", " ", " ", "X", "X", "X", "X"), after = 7) |>
-  insert_row(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
-  insert_row(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
-  insert_row(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)
+table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, digits = 2, coefs = c('Mate competition'='mate_compete', 'Job competition'='job_compete', 'Life satisfaction'='life_satisfaction'))
 
-table1
+table1 <- data.frame(table1)
+
+store1 <- table1[8:9,]
+store2 <- table1[10,]
+store2 <- store2$names
+
+table1 <- table1[-1,]
+table1 <- slice(table1, 1:(n() - 3))
+
+table1[nrow(table1) + 1,] <- c("Sociodemographics", " ", " ", "X", "X", "X", "X")
+table1[nrow(table1) + 1,] <- c("National attitudes toward refugees", " ", " ", " ", "X", "X", "X")
+table1[nrow(table1) + 1,] <- c("Local attitudes toward refugees", " ", " ", " ", " ", "X", "X")
+table1[nrow(table1) + 1,] <- c("Additional controls", " ", " ", " ", " ", " ", "X")
+
+table1t <- rbind(table1, store1)
+rownames(table1t) <- NULL
+colnames(table1t) <- c("name", "m1", "m2", "m3", "m4", "m5", "m6")
+
+table1t1 <- subset(table1t, select = -c(m4, m5, m6))
+table1t2 <- subset(table1t, select = -c(m1, m2, m3))
+
+table1t1 %>% 
+  kable(booktabs = T, col.names = c("", "Model 1", "Model 2", "Model 3"), align = "lccc") %>% 
+  kable_styling(latex_options="scale_down") %>% 
+  row_spec(0,bold=TRUE)
+
+table1t2 %>% 
+  kable(booktabs = T, col.names = c("", "Model 4", "Model 5", "Model 6"), align = "lccc") %>% 
+  kable_styling(latex_options="scale_down") %>% 
+  row_spec(0,bold=TRUE) %>% 
+  footnote(general = store2)
 

### 2023-02-19 outputs/paper/paper.qmd
Edits

--- 2023-02-18 outputs/paper/paper.qmd
@@
 
-Sociodemographics:
+Sociodemographics: \* Age Group \* Gender \* State \* German Citizen \* Marital Status \* Relationship status, single \* Religious Affiliation \* Education \* Occupation \* Income \* Household Size \* Subjective Social Status \* Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality \* Politics: left and right-leaning \* Politics: affiliated parties
 
--   Age Group
+Mate Competition: using a scale of agree or disagree \* Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
 
--   Gender
+Job Competition: using a scale of agree or disagree\
+\* The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
 
--   State
+Life Satisfaction: scale of 0-10 \* Satisfaction with life
 
--   German Citizen
+Encountering Refugees \* How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations
 
--   Marital Status
+Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree \* Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims \* Hostility against refugees justified \* Politicians should condemn attacks against refugees \* Racist violence is defensible if it leads to fewer refugees settling in a town \* Attacks against refugee homes are sometimes necessary to make garner the attention of politicians \* Refugee integration in Germany \* German refugees should be entitled to German citizenship \* The number of refugees should be reduced \* Refugees are receiving more than non-immigrant Germans \* Refugees should give up their culture to adopt that of Germany \* Refugees are good for the economy \* Refugees increase crime \* Increased refugees increase the risk of terrorism \* Will additional refugees in your town increase the influence of Islam (local) \* Will additional refugees in your town be a challenge for local schools (local) \* Will additional refugees in your town increase competition for housing (local) \* Will additional refugees in your town change the way of life in your town (local)
 
--   Relationship status, single
-
--   Religious Affiliation
-
--   Education
-
--   Occupation
-
--   Income
-
--   Household Size
-
--   Subjective Social Status
-
--   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
-
--   Politics: left and right-leaning
-
--   Politics: affiliated parties
-
-Mate Competition: using a scale of agree or disagree
-
--   Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
-
-Job Competition: using a scale of agree or disagree
-
--   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
-
-Life Satisfaction: scale of 0-10
-
--   Satisfaction with life
-
-Encountering Refugees
-
--   How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations
-
-Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree
-
--   Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims
-
--   Hostility against refugees justified
-
--   Politicians should condemn attacks against refugees
-
--   Racist violence is defensible if it leads to fewer refugees settling in a town
-
--   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians
-
--   Refugee integration in Germany
-
--   German refugees should be entitled to German citizenship
-
--   The number of refugees should be reduced
-
--   Refugees are receiving more than non-immigrant Germans
-
--   Refugees should give up their culture to adopt that of Germany
-
--   Refugees are good for the economy
-
--   Refugees increase crime
-
--   Increased refugees increase the risk of terrorism
-
--   Will additional refugees in your town increase the influence of Islam (local)
-
--   Will additional refugees in your town be a challenge for local schools (local)
-
--   Will additional refugees in your town increase competition for housing (local)
-
--   Will additional refugees in your town change the way of life in your town (local)
-
-Operational category
-
--   Experiment lists
-
--   Treatment lists
-
--   Outcome lists
-
--   Waves: out of 4
+Operational category \* Experiement lists \* Treatement lists \* Outcome lists \* Waves: out of 4
 
@@
 
-# Ethical Implications
+# \## Ethical Implications
 
@@
   theme(text=element_text(size=11, family="serif")) +
-  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =60)) +
+  ggtitle(wrapper("Nearly half of mating-aged men living in excess male areas perceive refugees as a threat to finding a partner", width =70)) +
   theme(plot.title = element_text(face = "bold"))
@@
 
-survey_data <- read_csv(here::here("inputs/data/survey_clean.csv"))
-
-s_stmt <- survey_data[survey_data$wave == 2,]
-s_stmt <- select(s_stmt, c(only_means, message, prevent, condemn, justified, list, treatment_list))
-
-s_stmt$meansp <- ifelse(s_stmt$only_means >= 3, 1, 0)
-s_stmt$msgp <- ifelse(s_stmt$message >= 3, 1, 0)
-s_stmt$prevp <- ifelse(s_stmt$prevent >= 3, 1, 0)
-s_stmt$justp <- ifelse(s_stmt$justified >= 3, 1, 0)
-
-s_stmtmeans <- s_stmt %>% 
-  na.omit(meansp)
-meansp <- mean(s_stmt$meansp)
-msgp <- mean(s_stmt$msgp)
-prevp <- mean(s_stmt$prevp)
-justp <- mean(s_stmt$justp)
+survey_w2 <- survey_data[survey_data$wave == 2,]
 
@@
 #| warning: false
-#| include: false
 

### 2023-02-19 outputs/paper/paper.qmd
edits

--- 2023-02-19 outputs/paper/paper.qmd
@@
 
+=======
 # Introduction
@@
 
+Sociodemographics: \* Age Group \* Gender \* State \* German Citizen \* Marital Status \* Relationship status, single \* Religious Affiliation \* Education \* Occupation \* Income \* Household Size \* Subjective Social Status \* Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality \* Politics: left and right-leaning \* Politics: affiliated parties
+
+Mate Competition: using a scale of agree or disagree \* Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
+
+Job Competition: using a scale of agree or disagree\
+\* The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
+
+Life Satisfaction: scale of 0-10 \* Satisfaction with life
+
+Encountering Refugees \* How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations
+
+Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree \* Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims \* Hostility against refugees justified \* Politicians should condemn attacks against refugees \* Racist violence is defensible if it leads to fewer refugees settling in a town \* Attacks against refugee homes are sometimes necessary to make garner the attention of politicians \* Refugee integration in Germany \* German refugees should be entitled to German citizenship \* The number of refugees should be reduced \* Refugees are receiving more than non-immigrant Germans \* Refugees should give up their culture to adopt that of Germany \* Refugees are good for the economy \* Refugees increase crime \* Increased refugees increase the risk of terrorism \* Will additional refugees in your town increase the influence of Islam (local) \* Will additional refugees in your town be a challenge for local schools (local) \* Will additional refugees in your town increase competition for housing (local) \* Will additional refugees in your town change the way of life in your town (local)
+
+Operational category \* Experiement lists \* Treatement lists \* Outcome lists \* Waves: out of 4
+
+# Discussion
+
+## Findings
+
+## Implications
+
+# \## Ethical Implications
+
+=======
 Sociodemographics:
@@
 -   Waves: out of 4
-
-# Discussion
-
-## Findings
-
-## Implications
-
-# Ethical Implications
-
-## Methodology
 

### 2023-02-19 outputs/paper/paper.qmd
Edits to data section and additional references

--- 2023-02-19 outputs/paper/paper.qmd
@@
 
-Sociodemographics:
+[Socio-demographics]{.underline}
 
 -   Age Group
-
 -   Gender
-
 -   State
-
 -   German Citizen
-
 -   Marital Status
-
 -   Relationship status, single
-
 -   Religious Affiliation
-
 -   Education
-
 -   Occupation
-
 -   Income
-
 -   Household Size
-
 -   Subjective Social Status
-
 -   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
-
 -   Politics: left and right-leaning
-
 -   Politics: affiliated parties
 
-Mate Competition: using a scale of agree or disagree
+[Mate Competition: using a scale of agree or disagree]{.underline}
 
 -   Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
-
-Job Competition: using a scale of agree or disagree
-
+-   Job Competition: using a scale of agree or disagree
 -   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
 
-Life Satisfaction: scale of 0-10
+[Life Satisfaction: scale of 0-10]{.underline}
 
@@
 
-Encountering Refugees
+[Encountering Refugees]{.underline}
 
--   How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations
+-   How many KM is the closest refugee reception center from your home
 
-Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree
+-   How many refugees do you believe have settled in your municipality in the last year
 
--   Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims
+-   In the last month, how many refugees have you encountered in the following locations
+
+[Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree]{.underline} -
+
+-   Violence is sometimes the only means that citizens have to get the attention of German politicians - Attitudes towards Muslims
 
@@
 
-Operational category
+[Operational category]{.underline}
 

### 2023-02-19 outputs/paper/paper.qmd
Structural edits
Edits to the introduction

@@
 In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
-Their findings for the estimand of non-immigrant German men suggest that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
-By using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increase anti-refugee sentiments and violence [@main_paper].
+Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
+Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper.
 
-Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
-In addressing the following two research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians, we conclude that \_\_\_\_\_\_\_\_INSERT CONCLUSION HERE\_\_\_\_\_.
+Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
+Our paper seeks to address the two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
+Our reproduction was conducted using the statistical programming language R [@citeR].
+To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra [@kableExtra.
 
@@
 
-[Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree]{.underline} -
+[Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree]{.underline}
 
@@
 # Results
-
-# Discussion
-
-## Findings
-
-## Implications
-
-## Ethical Implications
-
-In their paper, Dancygier, Egami, Jamal, and Rischke examine the ethical implication of using experimental methodologies to investigate their research topic.
-By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence.
-By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment, which might have been a possible outcome had trials been conducted [@main_paper].
-While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate.
-By being presented with a platform to express their perception of mate competition and if they agree that violence towards refugees is the only way to garner the attention of German politicians, respondents may feel that their opinions are incorrectly justified.
-This then has the potential to translate to violence towards German refugees.
-
-## Accounting for Bias
-
-Ethical implications and biases arise naturally when collecting quantitative and qualitative data.
-In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper].
-The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms.
-However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper].
-Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest.
-One method to control for this bias is simple random sampling, where participants are chosen by chance.
-Meaning that every individual in the population/ estimand has an equal chance of being selected.
-However, in their study, they were unable to utilize simple random sampling.
-Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and state/ geographical region [@main_paper}.
-Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].
-
-## Limitations
-
-## Future Research
 
@@
 
+# Discussion
+
+## Findings
+
+## Implications
+
+## Ethical Implications
+
+In their paper, Dancygier, Egami, Jamal, and Rischke examine the ethical implication of using experimental methodologies to investigate their research topic.
+By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence.
+By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment, which might have been a possible outcome had trials been conducted [@main_paper].
+While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate.
+By being presented with a platform to express their perception of mate competition and if they agree that violence towards refugees is the only way to garner the attention of German politicians, respondents may feel that their opinions are incorrectly justified.
+This then has the potential to translate to violence towards German refugees.
+
+## Accounting for Bias
+
+Ethical implications and biases arise naturally when collecting quantitative and qualitative data.
+In their paper, Dancygier, Egami, Jamal, and Rischke use online survey platforms to assess if Germans living in areas with greater populations of men who experience turmoil in the mating market are more likely to perceive competition between themselves and refugees, moreover, does this ideology predict hate crime support [@main_paper].
+The authors attempted to address ethical concerns and statistical biases by utilizing control groups and replicating their study with different samples and polling firms.
+However, one potential bias that is challenging to control for is the presence of sampling bias [@main_paper].
+Sampling bias occurs when participants in a study are not representative of the estimand or the ideal population of interest.
+One method to control for this bias is simple random sampling, where participants are chosen by chance.
+Meaning that every individual in the population/ estimand has an equal chance of being selected.
+However, in their study, they were unable to utilize simple random sampling.
+Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and state/ geographical region [@main_paper}.
+Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].
+
+## Limitations
+
+## Future Research
+
 \clearpage

### 2023-02-20 outputs/paper/paper.qmd
Grammar edits
Addition to the discussion

@@
 In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
+This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study.
 Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
-Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper.
+Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].
 
@@
 Our reproduction was conducted using the statistical programming language R [@citeR].
-To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra [@kableExtra.
+To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich \[sandwich\], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra \[@kableExtra.
 
@@
 
-## Implications
+In this paper, we have replicated the results found by Dancygier, Egami, Jamal, and Rischke.
+Their analysis sought to explore the correlation between perceived mate competition in municipalities with excess males and its contributions to anti-refugee sentiments and higher crime rates in Germany.
+Our paper has replicated two of their major claims.
+
+(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats
+
+(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians
+
+By replicating their results, we hope to apply a Canadian-facing lens to gain insights into Canadian dating markets, the geographical distribution of males and females and their potential impacts on anti-refugee sentiments.
+
+## Alberta: Investigating its population ratio, dating markets and anti-refugee sentiments
+
+To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females. 
+Alberta is a Province in Canada with a total population of 4,543,111 individuals.
+It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females, thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1 (cite stats 1).
+This means that there are about 11,000 more men than women residing in this Province.
+Part of the population gap can be explained by age, as Alberta has a primarily young population, we typically see that as populations age they exhibit a higher female population (cite Edmonton journal).
+Its trades centric economy also attracts male migrants from across Canada (cite Edmonton journal).
+Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of both males and females (cite Edmonton journal).
+However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women (cite statcan).
+Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term ‘mating-aged’ used in the original paper to describe higher tensions of dating competition.
+We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.
+While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence.
+However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta.
+Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees (cite alberta.ca).
+While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males (cite Edmonton journal).
+According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants (cite the globe and mail).
+However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees (cite the globe and mail).
+48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% (cite globe and mail).
+The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.
+We also see that in  Dancygier, Egami, Jamal, and Rischke's paper, they find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes (cite main paper).
+Based on these statistics, we believe that it is possible that Alberta can be experiencing a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.
+However, as stated in their original paper, far more research has to be conducted on this effect to get a better understanding of its implications on non-German countries.
 

### 2023-02-20 outputs/paper/paper.qmd
updates to paper written content

--- 2023-02-19 outputs/paper/paper.qmd
@@
 In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
+This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study.
 Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
-Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper.
+Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence \[@main_paper.
 
@@
 
--   Hostility against refugees justified
+-   Hostility against refugees is justified
 
@@
 
--   Refugee integration in Germany
+-   Refugees are integrating well into Germany
 
@@
 
-## Implications
-
 ## Ethical Implications

### 2023-02-20 outputs/paper/paper.qmd
Edits to bibliography

--- 2023-02-20 outputs/paper/paper.qmd
@@
 
-## Alberta: Investigating its population ratio, dating markets and anti-refugee sentiments
+## Alberta: Investigating its population ratios, dating markets and anti-refugee sentiments
 
@@
 Alberta is a Province in Canada with a total population of 4,543,111 individuals.
-It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females, thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1 (cite stats 1).
+It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females, thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1 [@statista].
 This means that there are about 11,000 more men than women residing in this Province.
-Part of the population gap can be explained by age, as Alberta has a primarily young population, we typically see that as populations age they exhibit a higher female population (cite Edmonton journal).
-Its trades centric economy also attracts male migrants from across Canada (cite Edmonton journal).
-Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of both males and females (cite Edmonton journal).
-However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women (cite statcan).
-Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term ‘mating-aged’ used in the original paper to describe higher tensions of dating competition.
+Part of the population gap can be explained by age, as Alberta has a primarily young population, we typically see that as populations age they exhibit a higher female population [@edmonton_journal].
+Its trades centric economy also attracts male migrants from across Canada [@edmonton_journal].
+Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of both males and females [@edmonton_journal].
+However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan].
+Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe higher tensions of dating competition.
 We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.
@@
 However, in addressing Albertan immigrant and refugee statistics we will aim to illustrate how these patterns found in Germany can manifest in the context of Alberta.
-Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees (cite alberta.ca).
-While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males (cite Edmonton journal).
-According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants (cite the globe and mail).
-However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees (cite the globe and mail).
-48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% (cite globe and mail).
+Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].
+While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal].
+According to a 2018 paper, at the time 6 in 10 Canadians disagreed when asked if immigration levels were too high, with 35% believing that Canada accepts too many immigrants [@globe_mail].
+However, sentiments appear less than positive in Alberta, with Albertans expressing harsher attitudes towards immigrants and refugees [@globe_mail].
+48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail].
 The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.
-We also see that in  Dancygier, Egami, Jamal, and Rischke's paper, they find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes (cite main paper).
+We also see that in Dancygier, Egami, Jamal, and Rischke's paper, they find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
 Based on these statistics, we believe that it is possible that Alberta can be experiencing a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.

### 2023-02-20 outputs/paper/paper.qmd
Structural edits

@@
 Our reproduction was conducted using the statistical programming language R [@citeR].
-To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich \[sandwich\], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra \[@kableExtra.
+To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra, [@kableExtra].
 
@@
 ```{r}
+
 #| label: tbl-terc
@@
 ```{r}
+
 #| label: fig-excess
@@
 ```{r}
+
 #| label: tbl-stmt
@@
 ```{r}
+
 #| label: fig-statements
@@
 ```{r}
+
 #| label: tbl-mate

### 2023-02-21 outputs/paper/paper.qmd

@@
 In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
-Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022].
+Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022, @macrotrends].
 
@@
 
+In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
+This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study.
+Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
+Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].
+
 Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
@@
 
-We will first discuss \_\_\_\_\_\_\_\_INSERT FORMT HERE\_\_\_\_\_\_\_\_\_\_
+We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction.
+We will then conduct a reproduction of their results to better improve upon the accessibility of their findings.
+Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.
 
@@
 
-(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats
+(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats.
 
-(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians
+(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
 
@@
 ## Future Research
+As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles (cite paper).
+They further call for tests in ethnonational countries and in regions where females overpopulate males to see if their findings apply to women (cite paper).
+As Global migration and refuge continue to increase, we anticipate that this field of study will become increasingly significant.
+It is thus crucial to expand on their findings to assess how they apply in varying nations.
+This is in hopes to create policy changes and account for preventative measures to avoid increased anti-refugee sentiments and hate crimes caused by sex-driven competition.
+We further hope for this field of research to be applied under less heteronormative circumstances and work to account for queer-identifying individuals.
 

### 2023-02-21 outputs/paper/paper.qmd
putting model table in landscape

@@
   pdf: 
+    include-in-header:
+        text: |
+           \usepackage{pdflscape}
     documentclass: article
@@
 # install.packages("kableExtra")
+
+library(bookdown)
 
@@
 
-```{r}
+```{r, message=FALSE, message=FALSE, echo=FALSE}
 
@@
 #| fig-cap: "Proportion of respondents who see refugees as a mating threat by age group and tercile"
-#| echo: false
-#| message: false
-#| warning: false
 
@@
 #| echo: false
-#| message: false
-#| warning: false
 
@@
 lm6 <- lm(as.formula(formula.6), data=survey_w4)
+```
 
+Finally, we reconstructed @main_paper's battery of linear models to predict respondents' sentiments toward refugee-directed hate crime.
+6 Models were trained with increasing numbers of factors weighted using Ordinary Least Squares @tbl-hatemodel.
+The first model used solely mate competition (measured by proportion of excess males).
+Our models grew in complexity such that the second version was inclusive of job competition and life satisfaction.
+In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added.
+Despite the addition of additional factors, across all models, the predictive weight of mate competition remains high.
+Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors.
+Life satisfaction's weight remains low across all inclusive models.
+Increasing R Squared indicates that model fit increases with additional factors in our model.
+These findings are consistent with @main_paper.
+
+\newpage
+
+\begin{landscape}
+
+```{r, message=FALSE, echo=FALSE, tidy=TRUE}
+
+#| label: tbl-hatemodel
+#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares.
+In parentheses are the standard errors.
+Asterisks denote ranges of p-values as described in the table footer."
+#| 
+table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, number_format = "%.3f", coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
+  set_escape_contents(FALSE) |>
+  add_rows(c("sociodemographics ", " ", " ", "X", "X", "X", "X"), after = 7)  |>
+  add_rows(c("national attitudes toward refugees", " ", " ", " ", "X", "X", "X"), after = 8) |>
+  add_rows(c("local attitudes toward refugees", " ", " ", " ", " ", "X", "X"), after = 9) |>
+  add_rows(c("additional controls", " ", " ", " ", " ", " ", "X"), after = 10)
+
+table1
+```
+
+\end{landscape}
+
+```{r, message=FALSE, message=FALSE, echo=FALSE, include=FALSE}
 table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, digits = 2, coefs = c('Mate competition'='mate_compete', 'Job competition'='job_compete', 'Life satisfaction'='life_satisfaction'))
@@
 ## Future Research
+
 As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles (cite paper).

### 2023-02-21 outputs/paper/paper.qmd
edit

@@
       text: |
-           \usepackage{pdflscape}
+        \usepackage{lscape}
+        \newcommand{\blandscape}{\begin{landscape}}
+        \newcommand{\elandscape}{\end{landscape}}
     documentclass: article
@@
 
-```{r, message=FALSE, message=FALSE, echo=FALSE}
+```{r, echo = FALSE, message = FALSE}
 
@@
 
-\begin{landscape}
+\blandscape
 
@@
 table1
+
 ```
 
-\end{landscape}
+\elandscape
 

### 2023-02-21 outputs/paper/paper.qmd
limitations section edits

@@
 Asterisks denote ranges of p-values as described in the table footer."
-#| 
+
 table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, number_format = "%.3f", coefs = c('mate competition'='mate_compete', 'job competition'='job_compete', 'life satisfaction'='life_satisfaction')) |>
@@
 
+Being a reproduction, much of our analysis was limited to the original survey circumstances captured in [@main_paper].
+Despite the survey being long, it can not be considered to be comprehensive.
+This prevented us from exploring other relationships in the data.
+For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War II.
+Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.
+
+ Due to the heteronormative nature of this study’s data, our analysis was also not able to be fully representative of the German population as [@main_paper]’s authors described.
+While this is not to be surprised from an ecological context of mating behaviour, perhaps gay men would have been found to experience anti-refugee sentiment as well as an extension of the mate competition argument.
+
+There were also limitations associated with missing and limited data in our set.
+For example, in our analysis depicted in @fig-excess, fewer than 300 observations were represented in the oldest age group, which these authors doubted was enough for a meaningful evaluation.
+
 ## Future Research

### 2023-02-22 outputs/paper/paper.qmd
Results section

@@
     number-sections: true
-
 output: 
@@
 bibliography: references.bib
-header-includes: \definecolor{ltgray}{HTML}{EFEFEF}
 ---
@@
 # install.packages("kableExtra")
-
-library(bookdown)
 
@@
 
-======= ##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings ======= ##Figure 1 not including p value, percentage bar graph, detailed explanation of tercile meanings
+Data from the 4th Wave of surveys were used to show correlation between someone answering that they perceive refugees as a threat to finding a romantic partner and that person's gender, age, and their municipality's gender ratio.
+We reconstructed the portion of the survey data used for this analysis in @fig-excess, changing the presentation to a comparative bar chart where we can directly, visually compare different categories' response patterns along a consistent y-axis.
 
-\clearpage
+@main_paper provides groupings for the varying elements that we wanted to distinguish and compare.
+The three age/gender groups compared are 1) All (men and women of all ages), 2) Men between ages of 18-44, and 3) Men of "mating age" (30-40), making them of an age that is most commonly seen as the range that people seek to find a partner and "settle down." There were also 3 different groupings for categorizing a municipality's gender ratio which are referred to as "Terciles." Gender ratio was calculated by dividing the male population by the female population of a given municipality [@main_paper].
+Within the survey data, each response had a value for that respondents' municipality's gender ratio.
+@tbl-terc shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd Terciles.
+
+Returning to @fig-excess, we immediately notice that the highest rate of perceiving refugees as threats, over 46%, is found in mating-aged men living in municipalities with relatively high male-to-female ratio (at least 1.12 men per 1 woman).
+Second is men ages 18-44 in the same tercile of municipalities at around 37%.
+This is in stark contrast to the All group which includes men and women of all ages, where the proportion is lowest in the 1st tercile at around 17%, and highest at the 3rd tercile with 23%.
+There is one exception of Men 30-40 in the 1st tercile, but otherwise, Men are consistently more likely to perceive refugees as threats to mating than the general population.
+This jumps greatly the higher the male-to-female ratio is in their own town; the rate in Men 30-40 is almost triple more in the 3rd tercile than the 1st, and about 1.8 times more than the 2nd.
+
+In analyzing @fig-excess, we can recognize that the combination of a person being a man, especially between the ages of 30-40, and living in a municipality that has about 9 men per 8 women does seem to predict a higher rate of that person believing that refugees are negatively affecting their chance at finding a romantic partner.
+To confirm, it is not necessarily true that these respondents are living in an area with disproportionately more refugee men, but men in general.
+Yet, there being more men at all in their town leads to them displacing blame on refugees when presented with a question regarding the topic.
 
@@
 
-```{r, message=FALSE, message=FALSE, echo=FALSE}
-
+```{r}
 #| label: tbl-terc
@@
 
-```{r, echo = FALSE, message = FALSE}
-
+```{r}
 #| label: fig-excess
 #| fig-cap: "Proportion of respondents who see refugees as a mating threat by age group and tercile"
+#| echo: false
+#| message: false
+#| warning: false
 
@@
 s_exc <- select(s_exc, c(gender, age, mate_compete, excess_males))
-s_exc <- na.omit(s_exc)
 
@@
 
-```{r, message=FALSE, message=FALSE, echo=FALSE}
-
+```{r}
 #| label: tbl-stmt
@@
 #| echo: false
+#| message: false
+#| warning: false
 
@@
 
-```{r, message=FALSE, message=FALSE, echo=FALSE}
+Shifting to the topic of hate crime and anti-refugee sentiments, another aspect of the survey asked the respondent to share whether they agreed or disagreed with varying statements that conveyed pro-hate crime or anti-refugee opinions.
+The exact statements the respondents were given can be seen in @tbl-stmt.
+For discussion, the statements have been shortened to "Only Means", "Message", "Justified", "Prevent", and "Condemn".
+The data set recorded whether respondents agreed with these statements.
+The last, Condemn, as seen in @tbl-stmt, is clearly an anti-hate crime statement.
+Thus, answers for this question were weight inversely, such that the data measures who disagreed with it.
 
+The visualization of what proportion of respondents agreed with given statements in the 2nd wave of surveys can be seen in @fig-statements.
+For unstated reasons, @main_paper excluded "Prevent" in their analysis despite having the data available to plot and analyze response rate for the statement.
+As evident, we have included it.
+We excluded the measurement for the control group of respondents who answered the Only Means statement in a list-format (as discussed in Methodology).
+This was originally intended to notice whether respondents may hide their true feelings about supporting violence against refugees if asked outright compared to if they were to be presented with it more passively in a list.
+As @main_paper found, there was no significant difference and this concern was proven to not have actually affected the regular survey data.
+Thus, we opted to only showcase the regular survey response rates.
+
+@fig-statements, shows that, for the first three statements (Only Means, Message, and Justified), between 17% and 20% of respondents agreed with the prompt.
+1 in 5 respondents specifically agreed that "hostility against refugees" that "leads to violence" can be justified in certain cases.
+The highest rate of agreement, though comes to the inverse of Condemn.
+Over 25%, more than 1 in 4 respondents, disagreed that there was a need for public figures to condemn hate crimes.
+This may point to a chunk of respondents not necessarily agreeing or supporting hate crime but not perceiving it as a major issue, and thus not seeing it as something that needs to be condemned.
+The other stand-out is how relatively low the agreement rate is for Prevent, being barely over 13%, 4% lower than the second lowest, Message.
+This may be due to the fact that Prevent is the only statement that pointedly uses the term "Xenophobic" to identify the intention of these violent acts, while the other statements use general language that don't assign an intrinsic moral value in their description of the violent acts.
+A respondent may not see a problem with any of the other statements, read Prevent, and simply disagree that their opinion is xenophobic, and thus disagree with it.
+It may have yielded more similar results to the other statements if it had been reworded to "Acts of violence against refugees".
+
+Analysis of @fig-excess confirms that there is a generally alarmingly high rate of support for hate-crime and anti-refugee statements, though there may be nuance in certain respondents not seeing these hate crimes as a problem or being racially motivated.
+These results supported the creation of @tbl-hatemodel discussed below.
+
+```{r}
 #| label: fig-statements
@@
 
-```{r, message=FALSE, message=FALSE, echo=FALSE}
+Finally, we reconstructed @main_paper's battery of linear models to predict respondents' sentiments toward refugee-directed hate crime.
+6 Models were trained with increasing numbers of factors weighted using Ordinary Least Squares @tbl-hatemodel.
+The first model used solely mate competition (measured by proportion of excess males).
+Our models grew in complexity such that the second version was inclusive of job competition and life satisfaction.
+In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added.
+Despite the addition of additional factors, across all models, the predictive weight of mate competition remains high.
+Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors.
+Life satisfaction's weight remains low across all inclusive models.
+Increasing R Squared indicates that model fit increases with additional factors in our model.
+These findings are consistent with @main_paper.
 
-#| label: tbl-mate
-#| tbl-cap: "Perceiving refugees as mate competition predicts support for hate crime"
+\newpage
+
+\blandscape
+
+```{r}
+#| label: tbl-hatemodel
+#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares.
+In parentheses are the standard errors.
+Asterisks denote ranges of p-values as described in the table footer."
 #| echo: false
@@
 lm6 <- lm(as.formula(formula.6), data=survey_w4)
-```
-
-Finally, we reconstructed @main_paper's battery of linear models to predict respondents' sentiments toward refugee-directed hate crime.
-6 Models were trained with increasing numbers of factors weighted using Ordinary Least Squares @tbl-hatemodel.
-The first model used solely mate competition (measured by proportion of excess males).
-Our models grew in complexity such that the second version was inclusive of job competition and life satisfaction.
-In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added.
-Despite the addition of additional factors, across all models, the predictive weight of mate competition remains high.
-Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors.
-Life satisfaction's weight remains low across all inclusive models.
-Increasing R Squared indicates that model fit increases with additional factors in our model.
-These findings are consistent with @main_paper.
-
-\newpage
-
-\blandscape
-
-```{r, message=FALSE, echo=FALSE, tidy=TRUE}
-
-#| label: tbl-hatemodel
-#| tbl-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares.
-In parentheses are the standard errors.
-Asterisks denote ranges of p-values as described in the table footer."
 
@@
 ```{r, message=FALSE, message=FALSE, echo=FALSE, include=FALSE}
+#| label: draft code (not used)
 table1 <- export_summs(lm1, lm2, lm3, lm4, lm5, lm6, scale = TRUE, digits = 2, coefs = c('Mate competition'='mate_compete', 'Job competition'='job_compete', 'Life satisfaction'='life_satisfaction'))
@@
 
-## Alberta: Investigating its population ratios, dating markets and anti-refugee sentiments
+## Canadian Relevance: Case Study on Alberta's population ratios, dating markets and anti-refugee sentiments
 
@@
 
- Due to the heteronormative nature of this study’s data, our analysis was also not able to be fully representative of the German population as [@main_paper]’s authors described.
+Due to the heteronormative nature of this study's data, our analysis was also not able to be fully representative of the German population as [@main_paper]'s authors described.
 While this is not to be surprised from an ecological context of mating behaviour, perhaps gay men would have been found to experience anti-refugee sentiment as well as an extension of the mate competition argument.

### 2023-02-22 outputs/paper/paper.qmd
edits to abstract

@@
     geometry: margin = 1in
-    abstract: "Globalization, immigration, and asylum seeking is a common topic of discussion, one which most people hold some personal opinion on accompanied by certain justifications.
-This paper analyzes data on what proportion of non-immigrant German men are likely to perceive refugees as threats to finding a romantic partner relative to the male-to-female ratio within their municipality and which of them support sentiments of anti-refugee violence.
+    abstract: "Globalization, immigration, and asylum seeking are common topics of discussion, which most people hold opinion due to certain personal justifications.
+This paper analyzes data on what proportion of non-immigrant German men are likely to perceive refugees as threats to finding a romantic partner relative to the male-to-female ratio within their municipality and their sentiments toward anti-refugee violence.
 Results show that there can be argued an effect of these sentiments on actual rates of hate crime.
 We apply secondary research regarding Canadian rates of immigration and gender imbalances and raise concerns regarding the possibly generalizable nature of the findings in Germany.
-As this issue specifically affects minority groups experiencing prejudice and even furthers their marginalization, we place great emphasis on the weight of this discussion and propose that it should be considered to inform policies or initiatives intending to address racism and hate crimes, especially in breaking down the framing of refugees as a threat to non-immigrants, whether that's through education, public messaging, or other implementations."
+As this issue specifically affects minority groups experiencing prejudice and even furthers their marginalization, we place great emphasis on the weight of this discussion and propose that it should be considered to inform policies or initiatives intending to address racism and hate crimes, especially in breaking down the framing of refugees as a threat to non-immigrants through education, public messaging, or other implementations."
     number-sections: true

### 2023-02-22 outputs/paper/paper.qmd
abstract edits

@@
     geometry: margin = 1in
-    abstract: "Globalization, immigration, and asylum seeking are common topics of discussion, which most people hold opinion due to certain personal justifications.
-This paper analyzes data on what proportion of non-immigrant German men are likely to perceive refugees as threats to finding a romantic partner relative to the male-to-female ratio within their municipality and their sentiments toward anti-refugee violence.
-Results show that there can be argued an effect of these sentiments on actual rates of hate crime.
-We apply secondary research regarding Canadian rates of immigration and gender imbalances and raise concerns regarding the possibly generalizable nature of the findings in Germany.
-As this issue specifically affects minority groups experiencing prejudice and even furthers their marginalization, we place great emphasis on the weight of this discussion and propose that it should be considered to inform policies or initiatives intending to address racism and hate crimes, especially in breaking down the framing of refugees as a threat to non-immigrants through education, public messaging, or other implementations."
+    abstract: "Immigration and asylum-seeking are common topics of discussion in our globalized world, about which many Westerners hold opinions due to certain personal justifications.
+This paper replicates data analysis of the perceptions of non-immigrant German males towards refugees in municipalities where males overpopulate females.
+We apply secondary research regarding Canadian rates of immigration and gender imbalances in Alberta and raise concerns regarding the possibly generalizable nature of the findings in Germany.
+As this issue specifically affects minority groups experiencing prejudice, we place great emphasis on the weight of this discussion and call for future investigations of this field to inform policies and initiatives to address racism and hate crimes."
     number-sections: true
@@
 Their analysis sought to explore the correlation between perceived mate competition in municipalities with excess males and its contributions to anti-refugee sentiments and higher crime rates in Germany.
-Our paper has replicated two of their major claims.
+Our paper has replicated two of their major findings.
 

### 2023-02-22 outputs/paper/paper.qmd
Grammar edits

@@
 These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
-Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets.
+Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets on anti-refugee sentiments.
 A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research [@main_paper].
@@
 Our paper will follow a reproduction of Dancygier, Egami, Jamal, and Rischke's findings and apply a Canadian-facing lens to discuss its implications on local Canadian populations and increased anti-refugee/ immigrant sentiments and violence.
-Our paper seeks to address the two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
+Our paper seeks to replicate their two following research claims, (1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats and (2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.
 Our reproduction was conducted using the statistical programming language R [@citeR].
@@
 
-The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany (cite paper).
-Our reproduction seeks to address two claims made from the original paper and apply a Canadian facing lens.
-The two claims are as follows: (1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
+The paper used for replication is from the American Journal of Political Science which follows a discussion on the correlation of perceived mate competition and its contributions to anti-refugee sentiments and higher crime rates in Germany [@main_paper].
+Our reproduction seeks to address two findings made from the original paper and apply a Canadian facing lens.
+
+Their two claims are as follows: (1) Are non-immigrant German men who live in municipalities with excess male populations more likely to perceive refugees as threats?
 (2) Are non-immigrant German men who perceive mate competition more likely to support violence as the only means to gain the attention of German politicians?
-To collect this data, the original paper uses four waves of online survey data collected in Germany that are representative of gender, age and state (geographic location) [@main_paper].
 
@@
 As a part of our reproduction, we also simplified the names of variables to make them easier to work with.
-From the original data, each variable correlates with a survey question asked to participants.
-To discuss the variables used in our reproduction I have grouped them in the following way and have listed each variable below.
+From the original survey data, each variable correlates with a survey question asked to participants.
+To discuss the variables used in our reproduction we have grouped them in the following way and have listed each variable below.
 
@@
 
--   Does the influx of male refugees make it difficult for non-immigrant german men to find female partners
+-   The influx of male refugees make it difficult for non-immigrant German men to find female partners
 -   Job Competition: using a scale of agree or disagree

### 2023-02-22 outputs/paper/paper.qmd
edits

--- 2023-02-22 outputs/paper/paper.qmd
@@
 In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
-Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022, @macrotrends].
+Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.
 

### 2023-02-22 outputs/paper/paper.qmd
edit

@@
 Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets on anti-refugee sentiments.
-A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research [@main_paper].
+A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research.
 

### 2023-02-22 outputs/paper/paper.qmd
edit

@@
 Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets on anti-refugee sentiments.
-A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research.
+A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.
 

### 2023-02-22 outputs/paper/paper.qmd
edit

@@
 These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
-Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets on anti-refugee sentiments.
+Despite this, one factor that has received little attention until recently is the impact of mate competition in dating and marriage markets on anti-refugee sentiments.
 A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.

### 2023-02-22 outputs/paper/paper.qmd
Edits

--- 2023-02-22 outputs/paper/paper.qmd
@@
 In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
-Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.
-
+Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022; @macrotrends].
+,
 There are many factors that contribute to the increase in hate crimes in Canada.
@@
 Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets on anti-refugee sentiments.
-A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research.
+A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research [@main_paper].
 
@@
 Alberta is a Province in Canada with a total population of 4,543,111 individuals.
-It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females, thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1 [@statista].
+It is the only Canadian Province that is more heavily populated by males, with a male population of 2,282,040 compared to 2,261,071 females [@statista].
+Thus having a ratio of approximately 1.01, which is comparable to that of the 1st tercile in Figure 1.
 This means that there are about 11,000 more men than women residing in this Province.
-Part of the population gap can be explained by age, as Alberta has a primarily young population, we typically see that as populations age they exhibit a higher female population [@edmonton_journal].
-Its trades centric economy also attracts male migrants from across Canada [@edmonton_journal].
-Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of both males and females [@edmonton_journal].
+Part of the population gap can be explained by age.
+Alberta has a primarily young population and we typically see that as populations age they exhibit a higher female population [@edmonton_journal].
+Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].
+Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal].
 However, according to the 2021 census, 101, 650 more males are single (not married or living common law and never married) than women [@govcan].
-Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe higher tensions of dating competition.
+Due to Alberta's young population, highly concentrated with men of working age, a comparison can be made to the term 'mating-aged' used in the original paper to describe males facing higher tensions of dating competition.
 We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.
@@
 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail].
-The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.
-We also see that in Dancygier, Egami, Jamal, and Rischke's paper, they find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
-Based on these statistics, we believe that it is possible that Alberta can be experiencing a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.
-However, as stated in their original paper, far more research has to be conducted on this effect to get a better understanding of its implications on non-German countries.
+The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
+Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.
+However, as stated in their original paper, we call for further research to be conducted on this effect to better understand its implications on non-German countries.
 
@@
 By using descriptive data in the form of surveys they are able to investigate the opinions of non-immigrant German males and their perception of mate competition and its translation to anti-refugee violence.
-By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment, which might have been a possible outcome had trials been conducted [@main_paper].
+By avoiding experimental trials, they were able to explore their topic without provoking anti-refugee sentiment [@main_paper].
 While conducting experimental trials on this topic of research is considered unethical, surveys and questionnaires may have a tendency to give respondents the impression that their opinions are commonly shared or even accurate.
@@
 One method to control for this bias is simple random sampling, where participants are chosen by chance.
-Meaning that every individual in the population/ estimand has an equal chance of being selected.
+Meaning that every individual in the population has an equal chance of being selected.
 However, in their study, they were unable to utilize simple random sampling.
-Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and state/ geographical region [@main_paper}.
+Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and geographical region [@main_paper].
 Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].
@@
 
-As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles (cite paper).
-They further call for tests in ethnonational countries and in regions where females overpopulate males to see if their findings apply to women (cite paper).
+As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles [@main_paper].
+They further call for tests in ethnonational countries and in regions where females overpopulate males to see if their findings apply to women [@main_paper].
 As Global migration and refuge continue to increase, we anticipate that this field of study will become increasingly significant.

### 2023-02-22 outputs/paper/paper.qmd
Edits

@@
 A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research [@main_paper].
+=======
+In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
+Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.
+
+There are many factors that contribute to the increase in hate crimes in Canada.
+However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada.
+These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
+Despite this, one factor that has received little attention until recently is the impact of mate competition in dating and marriage markets on anti-refugee sentiments.
+A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.
+>>>>>>> bca9bbc77a3d3c7b3af7a6d9319550b759e6f77f
 

### 2023-02-22 outputs/paper/paper.qmd
Edits
edits

@@
 In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
-Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022; @macrotrends].
-,
-There are many factors that contribute to the increase in hate crimes in Canada.
-However, with the rise of far-right discourse in the United States, anti-immigrant and anti-refugee rhetoric is becoming more prevalent in Canada.
-These negative attitudes and actions towards immigrants, refugees, and marginalized individuals can be the result of various structural and personal factors, including increased competition in the job and housing markets, resource scarcity, misguided beliefs about crime rates, illness, welfare dependency, and fears of losing national identity.
-Despite this, one factor that has received little attention until recently is the impact of competition in dating and marriage markets on anti-refugee sentiments.
-A 2021 paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this important and often-overlooked area of research [@main_paper].
-=======
-In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022].
 Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 [@government_of_canada_2022] and 130,125 refugees in 2020 [@macrotrends], these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents.
@@
 A [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischke published in the American Journal of Political Science delves into this potentially important and often-overlooked fusion of social science with ecology.
->>>>>>> bca9bbc77a3d3c7b3af7a6d9319550b759e6f77f
 
 In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
-This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study.
-Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
-Using ecological evidence and originally curated survey data, the paper concludes that competition in dating and marriage markets where men outnumber women increases anti-refugee sentiments and violence [@main_paper].
-
-In studying the opinions of German males living in municipalities with excess male populations, they find that a portion of non-immigrant German men hold the belief that refugees pose a threat to their ability to pursue German women [@main_paper].
-This population of individuals, non-immigrant German males in highly male populated municipalities being the estimand of the study.
+The study population is primarily non-immigrant German males in highly male populated municipalities.
+The estimand which we intend to replicate is the effect of mate competition on anti-refugee sentiments.
 Their finding suggests that hate crimes increase where non-immigrant German men are disadvantaged in their local dating markets [@main_paper].
@@
 Our reproduction was conducted using the statistical programming language R [@citeR].
-To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr], kableExtra, [@kableExtra].
+To further enable our analysis we employed the use of the following packages: readr [@readr], here [@here], readstata13 [@readstata13], MASS [@MASS], sandwich [@sandwich], lmtest [@lmtest], dplyr [@dplyr], tidyverse [@tidyverse], jtools [@jtools], huxtable [@huxtable], list [@list], knitr [@knitr] and kableExtra [@kableExtra].
 
 We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction.
-We will then conduct a reproduction of their results to better improve upon the accessibility of their findings.
+We will then conduct a reproduction of select results to verify their findings and improve upon their accessibility.
 Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.
@@
 
-This paper will replicate the survey data that was originally collected for the 2021 paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned.
-Using the online survey platform "Respondi", they conduct four waves of surveys which spanned from September 2016 to December 2017 [@main_paper].
+This paper will replicate the survey data that was originally collected for the [-@main_paper] paper by Dancygier, Egami, Jamal, and Rischkes, as previously mentioned.
+Using the online survey platform "Respondi", they conduct 4 waves of surveys which spanned from September 2016 to December 2017 [@main_paper].
 The researchers suggest that the anonymity provided by the online survey platform resulted in respondents answering more truthfully.
@@
 Age was then categorized by group which is as follows: 18-29, 30-39, 30-49, 50-59, and 60 and older.
-Both male and female participants took part in the survey, but females were only involved in the second and fourth waves of surveys.
+Both male and female participants took part in the survey, but females were only involved in Waves 2 and 4 of surveys.
 The survey was distributed across 16 German states.
@@
 From the original survey data, each variable correlates with a survey question asked to participants.
-To discuss the variables used in our reproduction we have grouped them in the following way and have listed each variable below.
+To discuss the variables used in our reproduction we have grouped them by category way and have listed each variable below.
+Some survey questions are presented, and have been reworded slightly for consistency and clarity.
 
@@
 -   Subjective Social Status
--   Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality
+-   Excess males: The proportion of males to females by states by dividing the number of women by men aged 14 and 44 for each municipality 
 -   Politics: left and right-leaning
@@
 
-[Mate Competition: using a scale of agree or disagree]{.underline}
+[Mate Competition: using a scale (1-4) to indicate agreement or disagreement]{.underline}
 
 -   The influx of male refugees make it difficult for non-immigrant German men to find female partners
--   Job Competition: using a scale of agree or disagree
--   The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs
+
+[Job Competition: using a scale of agree or disagree]{.underline}
+
+-   The inflow of young male refugees makes it more difficult for young non-immigrant German men to find work/ jobs
 
@@
 
--   Satisfaction with life
+-   Rank your satisfaction with life
 
@@
 
--   How many KM is the closest refugee reception center from your home
-
--   How many refugees do you believe have settled in your municipality in the last year
-
--   In the last month, how many refugees have you encountered in the following locations
+-   How many KM is the closest refugee reception center from your home?
+-   How many refugees do you believe have settled in your municipality in the last year?
+-   In the last month, how many refugees have you encountered in the following locations?
+(on the street, on public transport or in parks, in stores, in refugee reception centres or hostels, school, work)
 
@@
 
--   Violence is sometimes the only means that citizens have to get the attention of German politicians - Attitudes towards Muslims
-
+-   Violence is sometimes the only means that citizens have to get the attention of German politicians 
+-   Attitudes towards Muslims
 -   Hostility against refugees is justified
-
 -   Politicians should condemn attacks against refugees
-
 -   Racist violence is defensible if it leads to fewer refugees settling in a town
-
 -   Attacks against refugee homes are sometimes necessary to make garner the attention of politicians
-
 -   Refugees are integrating well into Germany
-
 -   German refugees should be entitled to German citizenship
-
 -   The number of refugees should be reduced
-
 -   Refugees are receiving more than non-immigrant Germans
-
 -   Refugees should give up their culture to adopt that of Germany
-
 -   Refugees are good for the economy
-
 -   Refugees increase crime
-
 -   Increased refugees increase the risk of terrorism
-
--   Will additional refugees in your town increase the influence of Islam (local)
-
--   Will additional refugees in your town be a challenge for local schools (local)
-
--   Will additional refugees in your town increase competition for housing (local)
-
--   Will additional refugees in your town change the way of life in your town (local)
+-   Additional refugees in your town will increase the influence of Islam (local)
+-   Additional refugees in your town will be a challenge for local schools (local)
+-   Additional refugees in your town will increase competition for housing (local)
+-   Additional refugees in your town will change the way of life in your town (local)
 
@@
 -   Experiment lists
-
 -   Treatment lists
-
 -   Outcome lists
-
 -   Waves: out of 4
@@
 
-Data from the 4th Wave of surveys were used to show correlation between someone answering that they perceive refugees as a threat to finding a romantic partner and that person's gender, age, and their municipality's gender ratio.
+Data from Wave 4 of surveys were used to show correlation between someone answering that they perceive refugees as a threat to finding a romantic partner and that person's gender, age, and their municipality's gender ratio.
 We reconstructed the portion of the survey data used for this analysis in @fig-excess, changing the presentation to a comparative bar chart where we can directly, visually compare different categories' response patterns along a consistent y-axis.
@@
 @main_paper provides groupings for the varying elements that we wanted to distinguish and compare.
-The three age/gender groups compared are 1) All (men and women of all ages), 2) Men between ages of 18-44, and 3) Men of "mating age" (30-40), making them of an age that is most commonly seen as the range that people seek to find a partner and "settle down." There were also 3 different groupings for categorizing a municipality's gender ratio which are referred to as "Terciles." Gender ratio was calculated by dividing the male population by the female population of a given municipality [@main_paper].
+The three age/gender groups compared are: (1) All (men and women of all ages), (2) Men between ages of 18-44, and (3) Men of "mating age" (30-40), making them of an age that is most commonly seen as the range that people seek to find a partner and "settle down." There were also 3 different groupings for categorizing a municipality's gender ratio which are referred to as "terciles." Gender ratio was calculated by dividing the male population by the female population of a given municipality [@main_paper].
 Within the survey data, each response had a value for that respondents' municipality's gender ratio.
-@tbl-terc shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd Terciles.
+@tbl-terc shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd terciles.
 
 Returning to @fig-excess, we immediately notice that the highest rate of perceiving refugees as threats, over 46%, is found in mating-aged men living in municipalities with relatively high male-to-female ratio (at least 1.12 men per 1 woman).
-Second is men ages 18-44 in the same tercile of municipalities at around 37%.
+Next is Men ages 18-44 in the same tercile of municipalities at around 37%.
 This is in stark contrast to the All group which includes men and women of all ages, where the proportion is lowest in the 1st tercile at around 17%, and highest at the 3rd tercile with 23%.
 There is one exception of Men 30-40 in the 1st tercile, but otherwise, Men are consistently more likely to perceive refugees as threats to mating than the general population.
-This jumps greatly the higher the male-to-female ratio is in their own town; the rate in Men 30-40 is almost triple more in the 3rd tercile than the 1st, and about 1.8 times more than the 2nd.
+This jumps greatly the higher the male-to-female ratio is in their own town; the rate in Men 30-40 is almost tripled in the 3rd tercile than the 1st, and about 1.8 times more than the 2nd.
 
@@
 To confirm, it is not necessarily true that these respondents are living in an area with disproportionately more refugee men, but men in general.
-Yet, there being more men at all in their town leads to them displacing blame on refugees when presented with a question regarding the topic.
+Yet, there being more men at all in their town might lead them to project blame onto refugees when presented with a question regarding the topic.
 
@@
 In the next four models, one at a time, sociodemographic factors, attitudes toward refugees (local first, then national), and last, additional factors (including perceptions of refugee settlements and political groups, and their affiliations) were added.
-Despite the addition of additional factors, across all models, the predictive weight of mate competition remains high.
+Despite the addition of factors, across all models, the predictive weight of mate competition remains high.
 Job competition, on the other hand, was introduced in model 2 with larger weight than mate competition, but it rapidly fell off with the introduction of more factors.
@@
 To investigate the relevance of Dancygier, Egami, Jamal, and Rischke's discoveries in a Canadian context, we will now explore Canada's only Province with a higher ratio of males than females.
+
 Alberta is a Province in Canada with a total population of 4,543,111 individuals.
@@
 Its trades centric economy also attracts young male migrants from across Canada [@edmonton_journal].
+
 Concerning the original paper, Alberta's population growth can be largely attributed to international immigration which has typically brought equal numbers of males and females [@edmonton_journal].
@@
 We thus believe that similar conditions for dating and marriage markets can be made between Alberta and the German municipalities of that the 1st Tercile from Figure 1.
+
 While population demographics are comparable between that of Alberta and the 1st tercile of German municipalities in the original paper, it is difficult to suggest that potential competition in Albertan dating and marriage markets correlates to anti-refugee sentiments and violence.
@@
 Based on the 2021-2022 Annual Population Report, Alberta welcomed 12,603 immigrants and 21,434 non-permanent residents, which include refugees [@alberta_2023].
+
 While previous accounts have suggested that immigration has brought an equal number of males and females, it is safe to assume that Alberta is a growing population, subject to a population with a higher concentration of males [@edmonton_journal].
@@
 48% of Albertans at the time agreed that refugee claims are not filed from real refugees, with 62% stating that immigrants do not adopt Canadian values, about 10% higher than the national average of 51% [@globe_mail].
-The globe and mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
+The Globe and Mail suggest that part of Alberta's higher anti-refugee attitudes can be attributed to its economy and fears of competition.Dancygier, Egami, Jamal, and Rischke  find that in areas where men significantly outnumber women, there are higher levels of anti-refugee hate crimes [@main_paper].
+
 Based on these statistics, we believe that Alberta may experience a similar effect of anti-refugee sentiments in part as a result of increased immigrants/ refugees and competition in a young male-dominated population.
@@
 However, in their study, they were unable to utilize simple random sampling.
-Instead attempted to make their survey results representative by conducting four waves of surveys meant to be representative of age, gender and geographical region [@main_paper].
+Instead attempted to make their survey results representative by conducting 4 waves of surveys meant to be representative of age, gender and geographical region [@main_paper].
 Despite their effort, their survey results may not be entirely representative as individuals who have a strong interest in the subject matter are more likely to participate, meaning they do not reflect the views of all non-immigrant German males [@main_paper].
@@
 This prevented us from exploring other relationships in the data.
-For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War II.
+For example, in this German context, it would have been interesting to look into sentiments toward the treatment of communities experiencing genocide during the history of World War 2.
 Our connection of findings to the Albertan context was also limited by this cultural and geographical separation from our data.
